---
title: "bffs_crossrunconn_01172025"
author: "Alicia Vallorani"
date: "2025-01-17"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if (!("pacman" %in% installed.packages()[,])) {
    install.packages("pacman")
  }
pacman::p_load(tidyverse, Hmisc, psych, lmerTest, sjPlot, officer, flextable,
               viridis, equatiomatic)

homepath <- "/Users/aliciavallorani/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Research Projects/F31/BFFs/analyses/cross_run_connectivity" 

source("/Users/aliciavallorani/Library/CloudStorage/Box-Box/Standard Codes/visualization_tools/basic_theme.R")
theme_set(basic_theme)

source("/Users/aliciavallorani/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Research Projects/Standard Codes/check_singularity.R")
```

# Data
```{r}
df_qst <- read.csv(file.path(homepath,
                             "/for_analysis/bffs_questionnaires_01192024.csv",
                             fsep = "")) |>
  select(dyad, id, ageVisit1, ageVisit2, weeksBetweenVisits, handedness, race, 
         ethnicity, sexAssigned, 
         genderIdentity, sexualIdentity, romAttract, sexAttract, siOverallVisit1, 
         siOverallVisit2, raRespondentAffection, uncomfortableWatchingSelf,
         saTotal) |>
  mutate(saTotalC = as.numeric(scale(saTotal, center = TRUE, scale = FALSE)))

df_dyadic_affect <- read.csv(file.path(homepath, 
                             "/for_analysis/bffs_crossrunconn_dyadicaffect_01172025.csv",
                             fsep = "")) |>
  full_join(df_qst) |>
  arrange(dyad, id, trial) |>
  # Filter dyads that didn't do bffs task
  filter(!dyad %in% c(1, 6, 18, 28, 31, 36)) |>
  # Filter ids missing both runs
  filter(!id %in% c(8, 18, 20, 30, 31, 38, 40, 47, 53)) |>
  # Filter ids missing either run
  filter(!id %in% c(9, 65, 66)) |>
  group_by(id) |>
  mutate(positiveBetween = mean(expressedPositiveProportion),
         positiveWithin = expressedPositiveProportion - positiveBetween,
         negativeBetween = mean(expressedNegativeProportion),
         negativeWithin = expressedNegativeProportion - negativeBetween,
         connectivitySelfBetween = mean(mentalizingConnectivitySelf),
         connectivitySelfWithin = mentalizingConnectivitySelf - connectivitySelfBetween) |>
  ungroup()

df_indi_affect <- read.csv(file.path(homepath, 
                             "/for_analysis/bffs_crossrunconn_individualaffect_01172025.csv",
                             fsep = "")) |>
  full_join(df_qst) |>
  arrange(dyad, id) |>
  # Filter dyads that didn't do bffs task
  filter(!dyad %in% c(1, 6, 18, 28, 31, 36)) |>
  # Filter ids missing both runs
  filter(!id %in% c(8, 18, 20, 30, 31, 38, 40, 47, 53)) |>
  # Filter ids missing either run
  filter(!id %in% c(9, 65, 66)) |>
  group_by(id) |>
  mutate(positiveSelfBetween = mean(expressedPositiveProportion),
         positiveSelfWithin = expressedPositiveProportion - positiveSelfBetween,
         negativeSelfBetween = mean(expressedNegativeProportion),
         negativeSelfWithin = expressedNegativeProportion - negativeSelfBetween,
         positiveFriendBetween = mean(expressedPositiveProportionFriend),
         positiveFriendWithin = expressedPositiveProportionFriend - positiveFriendBetween,
         negativeFriendBetween = mean(expressedNegativeProportionFriend),
         negativeFriendWithin = expressedNegativeProportionFriend - negativeFriendBetween,
         connectivitySelfBetween = mean(mentalizingConnectivitySelf),
         connectivitySelfWithin = mentalizingConnectivitySelf - connectivitySelfBetween) |>
  ungroup()

df_qst_sample <- df_dyadic_affect |>
  select(dyad, id, ageVisit1, ageVisit2, weeksBetweenVisits, handedness, race, 
         ethnicity, sexAssigned, 
         genderIdentity, sexualIdentity, romAttract, sexAttract, siOverallVisit1, 
         siOverallVisit2, raRespondentAffection, uncomfortableWatchingSelf,
         saTotal) |>
  unique()
```


# Demographics full sample
```{r}
# Race
df_qst |>
  group_by(race) |>
  summarise(n())

# Ethnicity
df_qst |>
  group_by(ethnicity) |>
  summarise(n())

# Sex Assigned
df_qst |>
  group_by(sexAssigned) |>
  summarise(n())

# Gender Identity
df_qst |>
  group_by(genderIdentity) |>
  summarise(n())

# Sexual Identity
df_qst |>
  group_by(sexualIdentity) |>
  summarise(n())
```


# Demographics partial sample
```{r}
# Race
df_qst_sample |>
  group_by(race) |>
  summarise(n())

# Ethnicity
df_qst_sample |>
  group_by(ethnicity) |>
  summarise(n())

# Sex Assigned
df_qst_sample |>
  group_by(sexAssigned) |>
  summarise(n())

# Gender Identity
df_qst_sample |>
  group_by(genderIdentity) |>
  summarise(n())

# Sexual Identity
df_qst_sample |>
  group_by(sexualIdentity) |>
  summarise(n())

# Sexual Identity
df_qst_sample |>
  group_by(handedness) |>
  summarise(n())
```


# Sample description
```{r}
# Full sample
psych::describe(df_qst |> select(ageVisit1, ageVisit2, weeksBetweenVisits, 
                                 romAttract, sexAttract))

# Partial sample
psych::describe(df_qst_sample |> select(ageVisit1, ageVisit2, weeksBetweenVisits,
                                        romAttract, sexAttract))
```


## Descriptives and correlations for between subjects measures
```{r}
# Describe
psych::describe(df_qst_sample |> select(saTotal, siOverallVisit1, siOverallVisit2,
                                  raRespondentAffection, uncomfortableWatchingSelf))

# Correlate 
rcorr(as.matrix(df_qst_sample |> select(saTotal, siOverallVisit1, siOverallVisit2,
                                  raRespondentAffection, uncomfortableWatchingSelf), 
                type = "pearson"))

# Distribution of Social Anxiety Scores
dist <- ggplot(df_qst_sample, aes(saTotal)) +
  geom_dotplot(binwidth = 8, dotsize = .9) +
  scale_x_continuous(breaks=seq(0, 100, 10), limits=c(0, 100)) +
  scale_y_continuous(NULL, breaks = NULL) +
  geom_vline(xintercept = 60) +
  labs(x = "Social Anxiety Symptoms")

dist

ggsave(file.path(homepath, "/output/sanxiety.png"), dist, height = 4, 
       width = 6, dpi = 300)
```

# Did dyadic affect impact connectivity across runs?
## Model
mlm1.3 best because not singular. Effect remains (even grows stronger) with
control variables included
```{r}
mlm1.1 <- with(df_dyadic_affect, lmer(mentalizingConnectivityFriend ~
                               connectivitySelfBetween + positiveBetween +
                                 negativeBetween +
                               connectivitySelfWithin*positiveWithin +
                               connectivitySelfWithin*negativeWithin +
                               (connectivitySelfWithin + positiveWithin + negativeWithin|dyad/id)))
check_singularity(mlm1.1)
summary(mlm1.1)

mlm1.2 <- with(df_dyadic_affect, lmer(mentalizingConnectivityFriend ~
                               connectivitySelfBetween + positiveBetween +
                                 negativeBetween +
                               connectivitySelfWithin*positiveWithin +
                               connectivitySelfWithin*negativeWithin +
                               (connectivitySelfWithin |dyad/id)))
check_singularity(mlm1.2)
summary(mlm1.2)

mlm1.3 <- with(df_dyadic_affect, lmer(mentalizingConnectivityFriend ~
                               connectivitySelfBetween + positiveBetween +
                                 negativeBetween +
                               connectivitySelfWithin*positiveWithin +
                               connectivitySelfWithin*negativeWithin +
                               (connectivitySelfWithin |id)))
summary(mlm1.3)
tab_model(mlm1.3, digits = 3, show.se = TRUE, show.stat = TRUE, show.ci = FALSE)

mlm1.3.c <- with(df_dyadic_affect, lmer(mentalizingConnectivityFriend ~
                                          uncomfortableWatchingSelf +
                                          siOverallVisit1 +
                                          siOverallVisit2 +
                                          raRespondentAffection +
                               connectivitySelfBetween + positiveBetween +
                                 negativeBetween +
                               connectivitySelfWithin*positiveWithin +
                               connectivitySelfWithin*negativeWithin +
                               (connectivitySelfWithin |id)))

summary(mlm1.3.c)
tab_model(mlm1.3.c, digits = 3, show.se = TRUE, show.stat = TRUE, show.ci = FALSE)
```


## Plot interaction
On trials where the proportion of expressed negative affect was >= .321 higher 
than average, higher mentalizing network connectivity during the Self Run was
associated with lower mentalizing network connectivity during the Friend Run.
```{r}
plot_mlm1.3 <- plot_model(mlm1.3, type = "pred", 
           terms = c("connectivitySelfWithin", "negativeWithin")) +
  ggtitle("") + 
  labs(y = "Connectivity During Friend Run",
       x = "Connectivity During Self Run",
       color = "Total Expressed Negative Affect") +
  scale_color_manual(labels = c("-1SD", "Mean", "+1SD"), 
                     values = c("#287C8E", "#440154", "#8FD744"),
                     drop = FALSE) +
  scale_fill_manual(labels = c("-1SD", "Mean", "+1SD"), 
                    values = c("#287C8E", "#440154", "#8FD744"), 
                    drop = FALSE)

plot_mlm1.3

ggsave(file.path(homepath, "/output/mlm1.3.png"), plot_mlm1.3, dpi = 300)


#johnson_neyman(model = mlm1.3, pred = connectivitySelfWithin, modx = negativeWithin)
```


# Was this moderated by social anxiety?
## Model
Effects remain with control variables
```{r}
mlm2 <- with(df_dyadic_affect, lmer(mentalizingConnectivityFriend ~
                               connectivitySelfBetween + positiveBetween +
                                 negativeBetween +
                               connectivitySelfWithin*positiveWithin*saTotalC +
                                 connectivitySelfWithin*negativeWithin*saTotalC +
                               (connectivitySelfWithin|id)))

summary(mlm2)
tab_model(mlm2, digits = 3, show.se = TRUE, show.stat = TRUE, show.ci = FALSE)

mlm2.c <- with(df_dyadic_affect, lmer(mentalizingConnectivityFriend ~
                                        uncomfortableWatchingSelf +
                                          siOverallVisit1 +
                                          siOverallVisit2 +
                                          raRespondentAffection +
                               connectivitySelfBetween + positiveBetween +
                                 negativeBetween +
                               connectivitySelfWithin*positiveWithin*saTotalC +
                                 connectivitySelfWithin*negativeWithin*saTotalC +
                               (connectivitySelfWithin|id)))

summary(mlm2.c)
tab_model(mlm2.c, digits = 3, show.se = TRUE, show.stat = TRUE, show.ci = FALSE)
```


## Plot Interaction
On trials higher in negative affect than average, participants higher in social
anxiety symptoms exhibited greater mentalizing network connectivity during the
friend run if they had higher connectivity during the self run. Conversely,
participants lower in social anxiety symptoms exhibited lower mentalizing
connectivity during the friend run if they had higher connectivity during the 
self run.
```{r}
# Low is 31.27; medium is 50.1; high is 68.92
plot_mlm2 <- plot_model(mlm2, type = "pred", 
           terms = c("connectivitySelfWithin", "negativeWithin", "saTotalC")) +
  ggtitle("") + 
  labs(y = "Connectivity During Friend Run",
       x = "Connectivity During Self Run",
       color = "Total Expressed Negative Affect") +
  scale_color_manual(labels = c("-1SD", "Mean", "+1SD"), 
                     values = c("#287C8E", "#440154", "#8FD744"),
                     drop = FALSE) +
  scale_fill_manual(labels = c("-1SD", "Mean", "+1SD"), 
                    values = c("#287C8E", "#440154", "#8FD744"), 
                    drop = FALSE)

plot_mlm2$data$facet <- ifelse(plot_mlm2$data$facet == "saTotalC = -18.21", 
                          "Social Anxiety = 31.27",
                          ifelse(plot_mlm2$data$facet == "saTotalC = 0.62",
                                 "Social Anxiety = 50.10",
                                 ifelse(plot_mlm2$data$facet == "saTotalC = 19.44",
                                        "Social Anxiety = 68.92", NA)))

plot_mlm2

ggsave(file.path(homepath, "/output/mlm2.png"), plot_mlm2, dpi = 300, 
       width = 9, height = 5)
```


# Was this specific to your own or friends affect?
## Model
Effects consistent but not significant with control variables 
```{r}
mlm3 <- with(df_indi_affect, lmer(mentalizingConnectivityFriend ~
                               connectivitySelfBetween + negativeSelfBetween +
                                 negativeFriendBetween + positiveSelfBetween + 
                                 positiveFriendBetween + 
                                 connectivitySelfWithin*positiveSelfWithin*saTotalC +
                                 connectivitySelfWithin*positiveFriendWithin*saTotalC +
                                 connectivitySelfWithin*negativeSelfWithin*saTotalC +
                                 connectivitySelfWithin*negativeFriendWithin*saTotalC +
                               (connectivitySelfWithin|id)))

summary(mlm3)
tab_model(mlm3, digits = 3, show.se = TRUE, show.stat = TRUE, show.ci = FALSE)

mlm3.c <- with(df_indi_affect, lmer(mentalizingConnectivityFriend ~
                                      uncomfortableWatchingSelf +
                                          siOverallVisit1 +
                                          siOverallVisit2 +
                                          raRespondentAffection +
                               connectivitySelfBetween + negativeSelfBetween +
                                 negativeFriendBetween + positiveSelfBetween + 
                                 positiveFriendBetween + 
                                 connectivitySelfWithin*positiveSelfWithin*saTotalC +
                                 connectivitySelfWithin*positiveFriendWithin*saTotalC +
                                 connectivitySelfWithin*negativeSelfWithin*saTotalC +
                                 connectivitySelfWithin*negativeFriendWithin*saTotalC +
                               (connectivitySelfWithin|id)))

summary(mlm3.c)
tab_model(mlm3.c, digits = 3, show.se = TRUE, show.stat = TRUE, show.ci = FALSE)
```


## Plot
The effect is potentially driven by the friend's negative affect expressions. 
Low anxiety individuals had lower mentalizing network connectivity during 
friend run on trials with higher than average negative affect and higher than 
average connectivity during self run. That is if their connectivity was high 
while watching their friend express negative affect, their connectivity was low
when watching themselves

High anxiety individuals had higher mentalizing connectivity during the friend
run on trials with higher than average negative affect and higher than average 
connectivity during self run. That is if their connectivity was high while 
watching their friend express negative affect, their connectivity was also high
while watching themselves.
```{r}
plot_mlm3 <- plot_model(mlm3, type = "pred", 
           terms = c("connectivitySelfWithin", "negativeFriendWithin", "saTotalC"))  +
  ggtitle("") + 
  labs(y = "Connectivity During Friend Run",
       x = "Connectivity During Self Run",
       color = "Friend Expressed Negative Affect") +
  scale_color_manual(labels = c("-1SD", "Mean", "+1SD"), 
                     values = c("#287C8E", "#440154", "#8FD744"),
                     drop = FALSE) +
  scale_fill_manual(labels = c("-1SD", "Mean", "+1SD"), 
                    values = c("#287C8E", "#440154", "#8FD744"), 
                    drop = FALSE)

plot_mlm3$data$facet <- ifelse(plot_mlm3$data$facet == "saTotalC = -18.21", 
                          "Social Anxiety = 31.27",
                          ifelse(plot_mlm3$data$facet == "saTotalC = 0.62",
                                 "Social Anxiety = 50.10",
                                 ifelse(plot_mlm3$data$facet == "saTotalC = 19.44",
                                        "Social Anxiety = 68.92", NA)))

plot_mlm3

ggsave(file.path(homepath, "/output/mlm3.png"), plot_mlm3, dpi = 300, 
       width = 9, height = 5)
```


# Equations for supplemental materials
```{r}
extract_eq(mlm1.3, wrap = TRUE, terms_per_line = 1, operator_location = "start")

extract_eq(mlm2, wrap = TRUE, terms_per_line = 1, operator_location = "start")

extract_eq(mlm3, wrap = TRUE, terms_per_line = 1, operator_location = "start")
```

