---
title: "BFFs Questionnaire Data Processing"
author: "Alicia Vallorani"
date: "2023-04-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if (!("pacman" %in% installed.packages()[,])) {
    install.packages("pacman")
  }
pacman::p_load(tidyverse, psych, Hmisc)

source("/Users/aliciavallorani/Library/CloudStorage/Box-Box/Standard Codes/visualization_tools/basic_theme.R")
theme_set(basic_theme)
```


# Visit 1 Questionnaires
## Data prep
```{r}
df_visit1 <- read.csv("/Users/aliciavallorani/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Research Projects/F31/BFFs/data_processing/questionnaires/final_raw_qst_data/bffs_visit1_qsts_04142023.csv") |>
  # Remove dayd 26 (dyad 26 did not follow instructions during the dyad)
  filter(id != "2337_26_51") |>
  filter(id != "2337_26_52") |>
  mutate_all(function(x) {
    if (is.character(x)) {
      case_when(
        x == "Do not wish to respond" ~ NA_character_,
        TRUE ~ x
      )
    } else {
      x
    }
  })
```


## Demographics
### Data prep
```{r}
demographics <- df_visit1 |>
  rename(visitDate1 = Timestamp, handedness = D2, sexAssigned = D3, 
         genderIdentity = D4, genderIdentityOther = D4.2, 
         sexualIdentity = D5, sexualIdentityOther = D5.2,
         race = D6, raceOther = D6.2, 
         ethnicity = D7, ethnicityOther = D7.2,
         romAttract = F1, sexAttract = F2) |>
  mutate(ageVisit1 = as.numeric(difftime(as.Date(visitDate1), as.Date(D1), 
                                         units ="days"))/365.25) |>
  dplyr::select(visitDate1, id, ageVisit1, handedness, race, raceOther, ethnicity, 
                ethnicityOther, sexAssigned, genderIdentity, genderIdentityOther, 
                sexualIdentity, sexualIdentityOther, romAttract, sexAttract)
```


### Sample demographics
```{r}
# age and romantic and sexual attraction
psych::describe(demographics |> dplyr::select(ageVisit1, romAttract, sexAttract))

# handedness
demographics |>
  group_by(handedness) |>
  summarise(n())

# sex assigned
demographics |>
  group_by(sexAssigned) |>
  summarise(n())

# gender
demographics |>
  group_by(genderIdentity) |>
  summarise(n())

# sexual identity
demographics %>%
  group_by(sexualIdentity) |>
  summarise(n())

# race
demographics |>
  group_by(race) |>
  summarise(n())

# ethnicity
demographics %>%
  group_by(ethnicity) |>
  summarise(n())
```


## Social interaction
### Data prep
```{r}
interaction <- df_visit1 |>
  dplyr::select(id, SI1, SI2, SI3, SI4, SI5, 
                SI6, SI7, SI8, SI9, SI10, SI11) |>
  rename_with(~paste0(.x, "Visit1"), starts_with("SI")) |>
  mutate(SI2Visit1r =
         recode(SI2Visit1, `1` = 8, `2` = 7, `3` = 5, `4` = 4, `5` = 3, `7` = 2, 
                `8` = 1)) |>
  rowwise() |>
  mutate(siQualityVisit1 = mean(c(SI1Visit1, SI2Visit1r, SI3Visit1, SI4Visit1, 
                            SI5Visit1, SI10Visit1, SI11Visit1)),
         siDisclosureVisit1 = mean(c(SI6Visit1, SI7Visit1)),
         siEngagementVisit1 = mean(c(SI8Visit1, SI9Visit1)),
         siOverallVisit1 = mean(c(SI1Visit1, SI2Visit1r, SI3Visit1, SI4Visit1, 
                            SI5Visit1, SI10Visit1, SI11Visit1, SI6Visit1, SI7Visit1,
                            SI8Visit1, SI9Visit1))) |>
     as.data.frame() 
```


### Descriptives
```{r}
psych::describe(interaction |> dplyr::select(siQualityVisit1, siDisclosureVisit1, 
                                             siEngagementVisit1))
 
rcorr(as.matrix(interaction |> dplyr::select(siQualityVisit1, siDisclosureVisit1, 
                                             siEngagementVisit1), type = "pearson")) 
```


### Internal reliability
```{r}
# Quality
interaction_quality_alpha <- interaction |>
  dplyr::select(SI1Visit1, SI2Visit1r, SI3Visit1, SI4Visit1, SI5Visit1, 
                SI10Visit1, SI11Visit1)

alpha(interaction_quality_alpha)

# Disclosure
interaction_disclosure_alpha <- interaction |>
  dplyr::select(SI6Visit1, SI7Visit1)

alpha(interaction_disclosure_alpha)

# Engagement
interaction_engagement_alpha <- interaction |>
  dplyr::select(SI8Visit1, SI9Visit1)

alpha(interaction_engagement_alpha)

# Overall
interaction_overall_alpha <- interaction |>
  dplyr::select(SI1Visit1, SI2Visit1r, SI3Visit1, SI4Visit1, SI5Visit1, 
                SI10Visit1, SI11Visit1, SI6Visit1, SI7Visit1, SI8Visit1, SI9Visit1)

alpha(interaction_overall_alpha)
```


## Social anxiety
### Data prep
```{r}
social_anxiety <- df_visit1 |>
  dplyr::select(id, LSAS1FearAnxiety, LSAS1Avoidance, LSAS2FearAnxiety, LSAS2Avoidance,	
                LSAS3FearAnxiety, LSAS3Avoidance, LSAS4FearAnxiety, LSAS4Avoidance,	
                LSAS5FearAnxiety, LSAS5Avoidance, LSAS6FearAnxiety, LSAS6Avoidance,
                LSAS7FearAnxiety, LSAS7Avoidance, LSAS8FearAnxiety, LSAS8Avoidance,
                LSAS9FearAnxiety, LSAS9Avoidance, LSAS10FearAnxiety, LSAS10Avoidance,
                LSAS11FearAnxiety, LSAS11Avoidance, LSAS12FearAnxiety, LSAS12Avoidance,
                LSAS13FearAnxiety, LSAS13Avoidance, LSAS14FearAnxiety, LSAS14Avoidance,
                LSAS15FearAnxiety, LSAS15Avoidance, LSAS16FearAnxiety, LSAS16Avoidance, 
                LSAS17FearAnxiety, LSAS17Avoidance, LSAS18FearAnxiety, LSAS18Avoidance,
                LSAS19FearAnxiety, LSAS19Avoidance, LSAS20FearAnxiety, LSAS20Avoidance,
                LSAS21FearAnxiety, LSAS21Avoidance, LSAS22FearAnxiety, LSAS22Avoidance,
                LSAS23FearAnxiety, LSAS23Avoidance, LSAS24FearAnxiety, LSAS24Avoidance) |>
  # Removing participant 28_56 who didn't complete the questionnaire
  filter(id != "2337_28_56") |>
  rowwise() |>
  mutate(across(.cols = (2:49), .fns = as.integer),
         saFearAnxiety = sum(LSAS1FearAnxiety, LSAS2FearAnxiety, LSAS3FearAnxiety,
                             LSAS4FearAnxiety, LSAS5FearAnxiety, LSAS6FearAnxiety,
                             LSAS7FearAnxiety, LSAS8FearAnxiety, LSAS9FearAnxiety,
                             LSAS10FearAnxiety, LSAS11FearAnxiety, LSAS12FearAnxiety,
                             LSAS13FearAnxiety, LSAS14FearAnxiety, LSAS15FearAnxiety,
                             LSAS16FearAnxiety, LSAS17FearAnxiety, LSAS18FearAnxiety,
                             LSAS19FearAnxiety, LSAS20FearAnxiety, LSAS21FearAnxiety,
                             LSAS22FearAnxiety, LSAS23FearAnxiety, LSAS24FearAnxiety),
         saAvoidance = sum(LSAS1Avoidance, LSAS2Avoidance, LSAS3Avoidance,
                           LSAS4Avoidance, LSAS5Avoidance, LSAS6Avoidance,
                           LSAS7Avoidance, LSAS8Avoidance, LSAS9Avoidance,
                           LSAS10Avoidance, LSAS11Avoidance, LSAS12Avoidance,
                           LSAS13Avoidance, LSAS14Avoidance, LSAS15Avoidance,
                           LSAS16Avoidance, LSAS17Avoidance, LSAS18Avoidance,
                           LSAS19Avoidance, LSAS20Avoidance, LSAS21Avoidance,
                           LSAS22Avoidance, LSAS23Avoidance, LSAS24Avoidance),
         saTotal = sum(saFearAnxiety, saAvoidance)) |>
  as.data.frame()
```


### Descriptives
```{r}
psych::describe(social_anxiety |> dplyr::select(saFearAnxiety, saAvoidance,
                                                saTotal))
 
rcorr(as.matrix(social_anxiety |> dplyr::select(saFearAnxiety, saAvoidance,
                                                saTotal), type = "pearson")) 

ggplot(social_anxiety, aes(saTotal)) +
  geom_histogram(bins = 10)
```


### Internal reliability
```{r}
social_anxiety_alpha <- social_anxiety |>
  dplyr::select(-id, -saFearAnxiety, -saAvoidance, -saTotal)

alpha(social_anxiety_alpha)
```


## Friendship functions
### Data prep
```{r}
# data.frame
friendship_functions <- df_visit1 |>
  dplyr::select(id, MFQFF1, MFQFF2, MFQFF3, MFQFF4, MFQFF5, MFQFF6, MFQFF7,
                MFQFF8, MFQFF9, MFQFF10, MFQFF11, MFQFF12, MFQFF13, MFQFF14,
                MFQFF15, MFQFF16, MFQFF17, MFQFF18, MFQFF19, MFQFF20, MFQFF21,
                MFQFF22, MFQFF23, MFQFF24, MFQFF25, MFQFF26, MFQFF27, MFQFF28,
                MFQFF29, MFQFF30) |>
  rowwise() |>
  mutate(MFQFF24 = as.numeric(MFQFF24),
         ffStimulatingCompanionship = mean(c(MFQFF4, MFQFF7, MFQFF18,
                                             MFQFF22, MFQFF28)),
         ffHelp = mean(c(MFQFF1, MFQFF9, MFQFF13, MFQFF24, MFQFF27)),
         ffIntimacy = mean(c(MFQFF3, MFQFF8, MFQFF15, MFQFF21, MFQFF29)),
         ffReliableAlliance = mean(c(MFQFF5, MFQFF12, MFQFF16, MFQFF20, MFQFF26)),
         ffSelfValidation = mean(c(MFQFF2, MFQFF11, MFQFF14, MFQFF23, MFQFF30)),
         ffEmotionalSecurity = mean(c(MFQFF6, MFQFF10, MFQFF17, MFQFF19, MFQFF25)),
         ffFriendshipFunctions = mean(c(MFQFF1, MFQFF2, MFQFF3, MFQFF4, MFQFF5,
                                        MFQFF6, MFQFF7, MFQFF8, MFQFF9, MFQFF10,
                                        MFQFF11, MFQFF12, MFQFF13, MFQFF14, 
                                        MFQFF15, MFQFF16, MFQFF17, MFQFF18,
                                        MFQFF19, MFQFF20, MFQFF21, MFQFF22,
                                        MFQFF23, MFQFF24, MFQFF25, MFQFF26,
                                        MFQFF27, MFQFF28, MFQFF29, MFQFF30))) |>
  as.data.frame()
```


### Descriptives
```{r}
psych::describe(friendship_functions |> dplyr::select(ffStimulatingCompanionship, ffHelp,
                                                      ffIntimacy, ffReliableAlliance,
                                                      ffSelfValidation, ffEmotionalSecurity))
 
rcorr(as.matrix(friendship_functions |> dplyr::select(ffStimulatingCompanionship, ffHelp,
                                                      ffIntimacy, ffReliableAlliance,
                                                      ffSelfValidation, ffEmotionalSecurity), 
                type = "pearson")) 
```


### Internal Reliability
```{r}
friendship_functions_alpha <- friendship_functions |>
  dplyr::select(MFQFF1, MFQFF2, MFQFF3, MFQFF4, MFQFF5, MFQFF6, MFQFF7, MFQFF8,
                MFQFF9, MFQFF10, MFQFF11, MFQFF12, MFQFF13, MFQFF14, MFQFF15,
                MFQFF16, MFQFF17, MFQFF18, MFQFF19, MFQFF20, MFQFF21, MFQFF22,
                MFQFF23, MFQFF24, MFQFF25, MFQFF26, MFQFF27, MFQFF28, MFQFF29,
                MFQFF30)

alpha(friendship_functions_alpha)
```


## Respondent affection
### Data prep
```{r}
respondent_affection <- df_visit1 |>
  dplyr::select(id, MFQRA1, MFQRA2, MFQRA3, MFQRA4, MFQRA5, MFQRA6, MFQRA7,
                MFQRA8, MFQRA9, MFQRA10, MFQRA11, MFQRA12, MFQRA13, MFQRA14,
                MFQRA15, MFQRA16) |>
  rowwise() |>
  mutate(raRespondentAffection = mean(c(MFQRA1, MFQRA2, MFQRA3, MFQRA4, MFQRA5,
                                        MFQRA6, MFQRA7, MFQRA8, MFQRA9, MFQRA10,
                                        MFQRA11, MFQRA12, MFQRA13, MFQRA14,
                                        MFQRA15, MFQRA16))) |>
  as.data.frame()
```


### Internal reliability
```{r}
respondent_affection_alpha <- respondent_affection |>
  dplyr::select(-id, -raRespondentAffection)

alpha(respondent_affection_alpha)
```


# Visit 2 Questionnaires 
## Data prep
```{r}
df_visit2 <- read.csv("/Users/aliciavallorani/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Research Projects/F31/BFFs/data_processing/questionnaires/final_raw_qst_data/bffs_visit2_qsts_04272023.csv") |>
  mutate_all(function(x) {
    if (is.character(x)) {
      case_when(
        x == "Do not wish to respond" ~ NA_character_,
        TRUE ~ x
      )
    } else {
      x
    }
  }) 

dob <- df_visit1 |>
  dplyr::select(id, D1) 

df_visit2 <- full_join(df_visit2, dob) |>
  mutate(Timestamp = ifelse(id =="2337_01_02", "2022-4-25", 
                            ifelse(id == "2337_06_11", "2022-3-29", 
                                   ifelse(id == "2337_06_12", "2022-3-31", 
                                          ifelse(id == "2337_18_35", "2022-12-3",
                                                 ifelse(id == "2337_18_36", "2022-12-6",
                                                        ifelse(id == "2337_19_38", "2022-11-9",
                                                               ifelse(id == "2337_27_53", "2023-3-16",
                                                                      ifelse(id == "2337_28_55", "2023-3-31",
                                                                             ifelse(id == "2337_28_56", "2023-4-11", 
                                                                                    ifelse(id == "2337_31_61", "2023-3-30",
                                                                                           ifelse(id == "2337_36_71", "2023-4-25", 
                                                                                                  ifelse(id == "2337_36_72", "2023-4-25", Timestamp)))))))))))),
       ageVisit2 = as.numeric(difftime(as.Date(Timestamp), as.Date(D1), 
                                  units ="days"))/365.25) |>
  rename(visitDate2 = Timestamp) 
```


## Social interaction
### Data prep
```{r}
df_visit2 <- df_visit2 |>
  rename_with(~paste0(.x, "Visit2"), starts_with("SI")) |>
  mutate(SI2Visit2r =
         recode(SI2Visit2, `1` = 8, `2` = 7, `3` = 5, `4` = 4, `5` = 3, `7` = 2, 
                `8` = 1)) |>
  rowwise() |>
  mutate(siQualityVisit2 = mean(c(SI1Visit2, SI2Visit2r, SI3Visit2, SI4Visit2, 
                            SI5Visit2, SI10Visit2, SI11Visit2)),
         siDisclosureVisit2 = mean(c(SI6Visit2, SI7Visit2)),
         siEngagementVisit2 = mean(c(SI8Visit2, SI9Visit2)),
         siOverallVisit2 = mean(c(SI1Visit2, SI2Visit2r, SI3Visit2, SI4Visit2, 
                                  SI5Visit2, SI10Visit2, SI11Visit2, SI6Visit2, 
                                  SI7Visit2, SI8Visit2, SI9Visit2))) |>
     as.data.frame() 
```


### Descriptives
```{r}
psych::describe(df_visit2 |> dplyr::select(siQualityVisit2, siDisclosureVisit2, 
                                           siEngagementVisit2))
 
rcorr(as.matrix(df_visit2 |> dplyr::select(siQualityVisit2, siDisclosureVisit2, 
                                           siEngagementVisit2), type = "pearson")) 
```


### Internal reliability
```{r}
# Quality
interaction_quality_alpha2 <- df_visit2 |>
  dplyr::select(SI1Visit2, SI2Visit2r, SI3Visit2, SI4Visit2, SI5Visit2, 
                SI10Visit2, SI11Visit2)

alpha(interaction_quality_alpha2)

# Disclosure
interaction_disclosure_alpha2 <- df_visit2 |>
  dplyr::select(SI6Visit2, SI7Visit2)

alpha(interaction_disclosure_alpha2)

# Engagement
interaction_engagement_alpha2 <- df_visit2 |>
  dplyr::select(SI8Visit2, SI9Visit2)

alpha(interaction_engagement_alpha2)

# Overall
interaction_overall_alpha2 <- df_visit2 |>
  dplyr::select(SI1Visit2, SI2Visit2r, SI3Visit2, SI4Visit2, SI5Visit2, 
                SI10Visit2, SI11Visit2, SI6Visit2, SI7Visit2, SI8Visit2, 
                SI9Visit2)

alpha(interaction_overall_alpha2)
```


# Merge and Export all questionnaires
```{r}
df_all <- Reduce(function(...) {full_join(...)}, list(demographics, 
                                                      interaction, 
                                                      social_anxiety, 
                                                      friendship_functions,
                                                      respondent_affection, 
                                                      df_visit2)) |>
  #filter(!is.na(visitDate1)) |> 
  mutate(weeksBetweenVisits = as.numeric(difftime(as.Date(visitDate2), as.Date(visitDate1), 
                                  units ="weeks"))) |>
  separate(id, c("study", "dyad", "id")) |>
  dplyr::select(dyad, id, ageVisit1, ageVisit2, weeksBetweenVisits, handedness, race, 
                raceOther, ethnicity, ethnicityOther, sexAssigned, genderIdentity, 
                genderIdentityOther, sexualIdentity, sexualIdentityOther, 
                romAttract, sexAttract, siQualityVisit1, siDisclosureVisit1, 
                siEngagementVisit1, saFearAnxiety, saAvoidance, saTotal, 
                ffStimulatingCompanionship, ffHelp, ffIntimacy, ffReliableAlliance, 
                ffSelfValidation, ffEmotionalSecurity, ffFriendshipFunctions, 
                raRespondentAffection, siQualityVisit2, siDisclosureVisit2, 
                siEngagementVisit2, uncomfortableWatchingSelf, amountEyesClosed,
                reasonEyesClosed, everything(), -study, -visitDate1, -visitDate2,
                -D1)

outpath <- "/Users/aliciavallorani/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Research Projects/F31/BFFs/data_processing/questionnaires/output"
write.csv(df_all, paste0(outpath, "/bffs_questionnaires_", 
                         format(Sys.time(), "%m%d%Y"), ".csv"), row.names = FALSE)
```

