---
title: "bffs_neuralsim_analyses_11212024"
author: "Alicia Vallorani"
date: "2024-11-21"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if (!("pacman" %in% installed.packages()[,])) {
    install.packages("pacman")
  }
pacman::p_load(tidyverse, psych, Hmisc, mice, miceadds, lmerTest, broom.mixed, 
               partR2, sjPlot, viridis, patchwork)

source("/Users/aliciavallorani/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Research Projects/Standard Codes/check_singularity.R")

source("/Users/aliciavallorani/Library/CloudStorage/Box-Box/Standard Codes/visualization_tools/basic_theme.R")
theme_set(basic_theme)

project_path <- "/Users/aliciavallorani/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Research Projects/F31/BFFs/analyses/neural_similarity" 

# QST data
qst_df <- read.csv(file.path(project_path,
                             "/data/for_analysis/bffs_questionnaires_01192024.csv", 
                             fsep = ""), stringsAsFactors = TRUE) |>
  # Adjust reported ethnicity
  mutate(ethnicity = recode(ethnicity, `Another ethnicity` = "Another ethnicity", 
                            `Hispanic/Latino/Latina/Latinx` = "Hispanic/Latino/Latina/Latinx", 
                            `Hispanic/Latino/Latina/Latinx, Non-Hispanic` =
                              "Hispanic/Latino/Latina/Latinx", 
                            `Non-Hispanic` = "Non-Hispanic", 
                            `Non-Hispanic, Unknown` = "Non-Hispanic",
                            `Unknown` = "Unknown"))

# Neural sim synchrony data
synchrony_df <- read.csv(file.path(project_path,
                             "/data/for_analysis/neural_similarity_ratings_allregions_data_11212024.csv", 
                             fsep = ""), stringsAsFactors = FALSE) |>
   mutate(neuralSimConditionCodes = as.factor(recode(neuralSimCondition,
                                                    "classic" = 0,
                                                    "self_perspective" = 1,
                                                    "friend_perspective" = 2)),
          atlasNameCodes = as.factor(recode(atlasName, "dmPFC" = 0, "vmPFC" = 1,
                                                       "rTPJ" = 2, "lTPJ" = 3))) |>
  # Disambigulate within and between variance
  group_by(dyad) |>
  mutate(traitRatings = mean(ratingsSim, na.rm = TRUE),
         stateRatings = ratingsSim - traitRatings) |>
  ungroup() |>
  left_join(qst_df) |>
  mutate(saTotalC = as.numeric(scale(saTotal, center = TRUE, scale = FALSE))) |>
  select(dyad, id, saTotal, saTotalC, atlasName, atlasNameCodes, clip, ratingsSim, 
         traitRatings, stateRatings, neuralSimCondition, neuralSimConditionCodes, 
         deconMeanCor, siOverallVisit1, siOverallVisit2, raRespondentAffection, 
         uncomfortableWatchingSelf) |>
  filter(!is.na(deconMeanCor))


# included ids
included_ids <- synchrony_df |> select(id) |> unique() |> left_join(qst_df)
```


# BFFs Neural Similarity Analyses

## Demographics full sample
```{r}
# Handedness
## 1 = Left; 2 = Right
qst_df |>
  group_by(handedness) |>
  summarise(n())

# Race
## 1 = Another race; 2 = Asian; 3 = Black; 4 = White; 5 = Mixed 
qst_df |>
  group_by(race) |>
  summarise(n())

# Ethnicity
## 1 = Another ethnicity; 2 = Hispanic/Latino/Latina/Latinx; 3 = Non-Hispanic; 
## 4 = Unknown
qst_df |>
  group_by(ethnicity) |>
  summarise(n())

# Sex Assigned
## 1 = Assigned female; 2 = Assigned male
qst_df |>
  group_by(sexAssigned) |>
  summarise(n())

# Gender Identity
## 1 = Man; 2 = Woman; 3 = Chose not to identify
qst_df |>
  group_by(genderIdentity) |>
  summarise(n())

# Sexual Identity
## 1 = Another identity; 2 = Bisexual; 3 = Heterosexual; 4 = Lesbian/Gay; 
## 5 = Chose not to identify
qst_df |>
  group_by(sexualIdentity) |>
  summarise(n())
```


## Demographics partial sample
```{r}
# Handedness
## 1 = Left; 2 = Right
included_ids |>
  group_by(handedness) |>
  summarise(n())

# Race
## 1 = Another race; 2 = Asian; 3 = Black; 4 = White; 5 = Mixed 
included_ids |>
  group_by(race) |>
  summarise(n())

# Ethnicity
## 1 = Another ethnicity; 2 = Hispanic/Latino/Latina/Latinx; 3 = Non-Hispanic; 
## 4 = Unknown
included_ids |>
  group_by(ethnicity) |>
  summarise(n())

# Sex Assigned
## 1 = Assigned female; 2 = Assigned male
included_ids |>
  group_by(sexAssigned) |>
  summarise(n())

# Gender Identity
## 1 = Man; 2 = Woman; 3 = Chose not to identify
included_ids |>
  group_by(genderIdentity) |>
  summarise(n())

# Sexual Identity
## 1 = Another identity; 2 = Bisexual; 3 = Heterosexual; 4 = Lesbian/Gay; 
## 5 = Chose not to identify
included_ids |>
  group_by(sexualIdentity) |>
  summarise(n())
```


## Sample description
```{r}
# Full sample
psych::describe(qst_df |> select(ageVisit1, ageVisit2, weeksBetweenVisits,
                                 romAttract, sexAttract))

# Partial sample
psych::describe(included_ids |> select(ageVisit1, ageVisit2, weeksBetweenVisits,
                                       romAttract, sexAttract))

# Social anxiety distribution
psych::describe(included_ids$saTotal)

dist <- ggplot(included_ids, aes(saTotal)) +
  geom_histogram()
```


## Descriptives and correlations for between subjects measures
```{r}
# Describe
psych::describe(included_ids |> select(saTotal, siOverallVisit1, siOverallVisit2,
                                       raRespondentAffection, 
                                       uncomfortableWatchingSelf))

# Correlate 
rcorr(as.matrix(included_ids |> select(saTotal, siOverallVisit1, siOverallVisit2,
                                       raRespondentAffection, 
                                       uncomfortableWatchingSelf), 
                type = "pearson"))

# Distribution of Social Anxiety Scores
dist <- ggplot(included_ids, aes(saTotal)) +
  geom_dotplot(binwidth = 8, dotsize = .9) +
  scale_x_continuous(breaks=seq(10, 90, 10), limits=c(10, 90)) +
  scale_y_continuous(NULL, breaks = NULL) +
  geom_vline(xintercept = 60) +
  labs(x = "Social Anxiety Symptoms")

ggsave("/Users/aliciavallorani/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Research Projects/F31/BFFs/analyses/neural_similarity/output/figures/dist.png", plot = dist, 
       width = 10, height = 6)
```


## Multiple imputation
```{r}
# All data
imputed_df <- mice(synchrony_df, m = 25, maxit = 50, method = 'pmm', 
                   seed = 500, print = FALSE)

# Split imputed data for region analyses
imputed_datasets <- lapply(1:25, function(i) complete(imputed_df, i))

split_datasets <- lapply(imputed_datasets, function(df) {
  split(df, df$atlasName) 
})

combine_splits <- function(group_name) {
  lapply(split_datasets, function(group_list) group_list[[group_name]])
}

dmPFC_data <- combine_splits("dmPFC")
vmPFC_data <- combine_splits("vmPFC")
rTPJ_data <- combine_splits("rTPJ")
lTPJ_data <- combine_splits("lTPJ")


# dmPFC & rTPJ
dmPFC_rTPJ_data <- lapply(imputed_datasets, function(df) {
  df[df$atlasName %in% c("dmPFC", "rTPJ"), ] 
})

# vmPFC & lTPJ
vmPFC_lTPJ_data <- lapply(imputed_datasets, function(df) {
  df[df$atlasName %in% c("vmPFC", "lTPJ"), ] 
})

# dmPFC, vmPFD and rTPJ
dmPFC_vmPFC_rTPJ_data <- lapply(imputed_datasets, function(df) {
  df[df$atlasName %in% c("dmPFC", "vmPFC", "rTPJ"), ] 
})
```


## Multilevel models
### Affective similarity and social anxiety
```{r}
options(digits = 5, scipen = 999)
# listwise deleted
mlm1s <- with(synchrony_df, lmer(deconMeanCor ~
                                 traitRatings + atlasNameCodes +
                                 stateRatings*neuralSimConditionCodes*saTotalC +
                                 (stateRatings|dyad)))

summary(mlm1s)

# imputed
mlm1i <- with(imputed_df, lmer(deconMeanCor ~
                               traitRatings + atlasNameCodes +
                               stateRatings*neuralSimConditionCodes*saTotalC +
                               (1|dyad)))

summary(pool(mlm1i)) |> mutate(across(where(is.numeric), ~ round(., 3))) 

mlm1i_random_effects_list <- lapply(1:25, function(i) {
  model <- lmer(deconMeanCor ~
                traitRatings + atlasNameCodes +
                stateRatings*neuralSimConditionCodes*saTotalC +
                (stateRatings|dyad),
                data = imputed_datasets[[i]])
  
  # Extract the random effects information and return as a data frame
  data.frame(model = i, as.data.frame(summary(model)$varcor))
})

combined_df <- bind_rows(mlm1i_random_effects_list) |>
  unite(item, c("grp", "var1", "var2")) |>
  mutate(item = str_replace_all(item, fixed("NA"), ""),
         item = str_replace_all(item, fixed("("), ""),
         item = str_replace_all(item, fixed(")"), ""),
         item = str_replace_all(item, fixed("_"), ""))

combined_df |>
  group_by(item) |>
  mutate(vcov_mean = mean(vcov),
         sdcor_mean = mean(sdcor)) |>
  select(item, vcov_mean, sdcor_mean) |>
  unique()

# with control variables
mlm1ic <- with(imputed_df, lmer(deconMeanCor ~
                                uncomfortableWatchingSelf +
                                siOverallVisit1 +
                                siOverallVisit2 +
                                raRespondentAffection +
                                traitRatings + atlasNameCodes +
                                stateRatings*neuralSimConditionCodes*saTotalC +
                                (1|dyad)))

summary(pool(mlm1ic)) |> mutate(across(where(is.numeric), ~ round(., 3))) 

mlm1ic_random_effects_list <- lapply(1:25, function(i) {
  model <- lmer(deconMeanCor ~
                uncomfortableWatchingSelf +
                siOverallVisit1 +
                siOverallVisit2 +
                raRespondentAffection +
                traitRatings + atlasNameCodes +
                stateRatings*neuralSimConditionCodes*saTotalC +
                (stateRatings|dyad),
                data = imputed_datasets[[i]])
  
  # Extract the random effects information and return as a data frame
  data.frame(model = i, as.data.frame(summary(model)$varcor))
})

combined_df <- bind_rows(mlm1ic_random_effects_list) |>
  unite(item, c("grp", "var1", "var2")) |>
  mutate(item = str_replace_all(item, fixed("NA"), ""),
         item = str_replace_all(item, fixed("("), ""),
         item = str_replace_all(item, fixed(")"), ""),
         item = str_replace_all(item, fixed("_"), ""))

combined_df |>
  group_by(item) |>
  mutate(vcov_mean = mean(vcov),
         sdcor_mean = mean(sdcor)) |>
  select(item, vcov_mean, sdcor_mean) |>
  unique()
```


### Affective similarity without social anxiety
```{r}
mlm2i <- with(imputed_df, lmer(deconMeanCor ~
                               traitRatings + atlasNameCodes +
                               stateRatings*neuralSimConditionCodes +
                               (1|dyad)))

summary(pool(mlm2i)) |> mutate(across(where(is.numeric), ~ round(., 3))) 

mlm2i_random_effects_list <- lapply(1:25, function(i) {
  model <- lmer(deconMeanCor ~
                traitRatings + atlasNameCodes +
                stateRatings*neuralSimConditionCodes +
                (stateRatings|dyad),
                data = imputed_datasets[[i]])
  
  # Extract the random effects information and return as a data frame
  data.frame(model = i, as.data.frame(summary(model)$varcor))
})

combined_df <- bind_rows(mlm2i_random_effects_list) |>
  unite(item, c("grp", "var1", "var2")) |>
  mutate(item = str_replace_all(item, fixed("NA"), ""),
         item = str_replace_all(item, fixed("("), ""),
         item = str_replace_all(item, fixed(")"), ""),
         item = str_replace_all(item, fixed("_"), ""))

combined_df |>
  group_by(item) |>
  mutate(vcov_mean = mean(vcov),
         sdcor_mean = mean(sdcor)) |>
  select(item, vcov_mean, sdcor_mean) |>
  unique()
```


### Mentalizing region and perspective
```{r}
mlm3i <- with(imputed_df, lmer(deconMeanCor ~
                               atlasNameCodes*neuralSimConditionCodes +
                               (1|dyad)))

summary(pool(mlm3i)) |> mutate(across(where(is.numeric), ~ round(., 3))) 

mlm3i_random_effects_list <- lapply(1:25, function(i) {
  model <- lmer(deconMeanCor ~
                atlasNameCodes*neuralSimConditionCodes +
                (1|dyad),
                data = imputed_datasets[[i]])
  
  # Extract the random effects information and return as a data frame
  data.frame(model = i, as.data.frame(summary(model)$varcor))
})

combined_df <- bind_rows(mlm1i_random_effects_list) |>
  unite(item, c("grp", "var1", "var2")) |>
  mutate(item = str_replace_all(item, fixed("NA"), ""),
         item = str_replace_all(item, fixed("("), ""),
         item = str_replace_all(item, fixed(")"), ""),
         item = str_replace_all(item, fixed("_"), ""))

combined_df |>
  group_by(item) |>
  mutate(vcov_mean = mean(vcov),
         sdcor_mean = mean(sdcor)) |>
  select(item, vcov_mean, sdcor_mean) |>
  unique()
```


#### Plot interactions
```{r}
# Interaction between shared affect and perspective
int1 <- plot_model(mlm1s, type = "pred", 
           terms = c("stateRatings", "neuralSimConditionCodes")) +
  ggtitle("") + 
  labs(y = "Neural Similarity",
       x = "Affective Similarity",
       color = "Condition") +
  scale_color_manual(labels = c("Same-Stimuli", "Self-Perspective", "Friend-Perspective"), 
                     values = c("#287C8E", "#440154", "#8FD744"),
                     drop = FALSE) +
  scale_fill_manual(labels = c("Same-Stimuli", "Self-Perspective", "Friend-Perspective"), 
                    values = c("#287C8E", "#440154", "#8FD744"), 
                    drop = FALSE)

ggsave("/Users/aliciavallorani/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Research Projects/F31/BFFs/analyses/neural_similarity/output/figures/int1.png", plot = int1, 
       width = 10, height = 6) 


# Interaction between shared affect, perspective and social anxiety symptoms
int2 <- plot_model(mlm1s, type = "pred", 
           terms = c("stateRatings", "neuralSimConditionCodes", "saTotalC")) +
  ggtitle("") + 
  labs(y = "Neural Similarity",
       x = "Affective Similarity",
       color = "Condition") +
  scale_color_manual(labels = c("Same-Stimuli", "Self-Perspective", "Friend-Perspective"), 
                     values = c("#287C8E", "#440154", "#8FD744"),
                     drop = FALSE) +
  scale_fill_manual(labels = c("Same-Stimuli", "Self-Perspective", "Friend-Perspective"), 
                    values = c("#287C8E", "#440154", "#8FD744"), 
                    drop = FALSE)

# Average social anxiety 48.85
int2$data$facet <- ifelse(int2$data$facet == "saTotalC = -18.41", 
                          "Social Anxiety = 30.44",
                          ifelse(int2$data$facet == "saTotalC = 1.24",
                                 "Social Anxiety = 50.09",
                                 ifelse(int2$data$facet == "saTotalC = 20.89",
                                        "Social Anxiety = 69.74", NA)))

ggsave("/Users/aliciavallorani/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Research Projects/F31/BFFs/analyses/neural_similarity/output/figures/int2.png", plot = int2, 
       width = 10, height = 6)
```


### Test by region
#### listwise deleted
```{r}
# dmPFC
dmpfc <- synchrony_df |> filter(atlasName == "dmPFC")
dmpfc_model <- with(dmpfc, lmer(deconMeanCor ~ traitRatings +
                                stateRatings*neuralSimConditionCodes*saTotalC +
                                (1|dyad)))

summary(dmpfc_model)

# vmPFC
vmpfc <- synchrony_df |> filter(atlasName == "vmPFC")
vmpfc_model <- with(vmpfc, lmer(deconMeanCor ~ traitRatings +
                                stateRatings*neuralSimConditionCodes*saTotalC +
                                (1|dyad)))

summary(vmpfc_model)

# rTPJ - result possibly driven by rTPJ
rtpj <- synchrony_df |> filter(atlasName == "rTPJ")
rtpj_model <- with(rtpj, lmer(deconMeanCor ~ traitRatings +
                              stateRatings*neuralSimConditionCodes*saTotalC +
                              (1|dyad)))

summary(rtpj_model)

# lTPJ
ltpj <- synchrony_df |> filter(atlasName == "lTPJ")
ltpj_model <- with(ltpj, lmer(deconMeanCor ~ traitRatings +
                              stateRatings*neuralSimConditionCodes*saTotalC +
                              (1|dyad)))

summary(ltpj_model)
```


#### Without social anxiety
dmpfc - stateRatings X neuralSimCondition1
```{r}
# dmpfc - stateRatings:neuralSimConditionCodes1	0.036214492	0.017003753	0.04246925
model_results <- lapply(1:25, function(i) {
  model <- lmer(deconMeanCor ~
                  traitRatings +
                  stateRatings*neuralSimConditionCodes +
                  (1 | dyad),
                data = dmPFC_data[[i]])
  
  # Extract coefficients and p-values
  summary_data <- coef(summary(model))
  data.frame(
    Term = rownames(summary_data),
    Estimate = summary_data[, "Estimate"],
    SE = summary_data[, "Std. Error"],
    t_value = summary_data[, "t value"],
    p_value = summary_data[, "Pr(>|t|)"]
  )
})

reduce(model_results, full_join, by = "Term") %>%
  mutate(
    Mean_Estimate = rowMeans(select(., starts_with("Estimate")), na.rm = TRUE),
    Mean_SE = rowMeans(select(., starts_with("SE")), na.rm = TRUE),
    Mean_t_value = rowMeans(select(., starts_with("t_value")), na.rm = TRUE),
    Mean_p_value = rowMeans(select(., starts_with("p_value")), na.rm = TRUE)
  ) %>%
  select(Term, Mean_Estimate, Mean_SE, Mean_t_value, Mean_p_value)

# vmpfc
model_results <- lapply(1:25, function(i) {
  model <- lmer(deconMeanCor ~
                  traitRatings +
                  stateRatings*neuralSimConditionCodes +
                  (1 | dyad),
                data = vmPFC_data[[i]])
  
  # Extract coefficients and p-values
  summary_data <- coef(summary(model))
  data.frame(
    Term = rownames(summary_data),
    Estimate = summary_data[, "Estimate"],
    SE = summary_data[, "Std. Error"],
    t_value = summary_data[, "t value"],
    p_value = summary_data[, "Pr(>|t|)"]
  )
})

reduce(model_results, full_join, by = "Term") %>%
  mutate(
    Mean_Estimate = rowMeans(select(., starts_with("Estimate")), na.rm = TRUE),
    Mean_SE = rowMeans(select(., starts_with("SE")), na.rm = TRUE),
    Mean_t_value = rowMeans(select(., starts_with("t_value")), na.rm = TRUE),
    Mean_p_value = rowMeans(select(., starts_with("p_value")), na.rm = TRUE)
  ) %>%
  select(Term, Mean_Estimate, Mean_SE, Mean_t_value, Mean_p_value)

# rtpj - stateRatings:neuralSimConditionCodes1	0.0331999289	0.017428905	0.07470767
model_results <- lapply(1:25, function(i) {
  model <- lmer(deconMeanCor ~
                  traitRatings +
                  stateRatings*neuralSimConditionCodes +
                  (1 | dyad),
                data = rTPJ_data[[i]])
  
  # Extract coefficients and p-values
  summary_data <- coef(summary(model))
  data.frame(
    Term = rownames(summary_data),
    Estimate = summary_data[, "Estimate"],
    SE = summary_data[, "Std. Error"],
    t_value = summary_data[, "t value"],
    p_value = summary_data[, "Pr(>|t|)"]
  )
})

reduce(model_results, full_join, by = "Term") %>%
  mutate(
    Mean_Estimate = rowMeans(select(., starts_with("Estimate")), na.rm = TRUE),
    Mean_SE = rowMeans(select(., starts_with("SE")), na.rm = TRUE),
    Mean_t_value = rowMeans(select(., starts_with("t_value")), na.rm = TRUE),
    Mean_p_value = rowMeans(select(., starts_with("p_value")), na.rm = TRUE)
  ) %>%
  select(Term, Mean_Estimate, Mean_SE, Mean_t_value, Mean_p_value)

# ltpj
model_results <- lapply(1:25, function(i) {
  model <- lmer(deconMeanCor ~
                  traitRatings +
                  stateRatings*neuralSimConditionCodes +
                  (1 | dyad),
                data = lTPJ_data[[i]])
  
  # Extract coefficients and p-values
  summary_data <- coef(summary(model))
  data.frame(
    Term = rownames(summary_data),
    Estimate = summary_data[, "Estimate"],
    SE = summary_data[, "Std. Error"],
    t_value = summary_data[, "t value"],
    p_value = summary_data[, "Pr(>|t|)"]
  )
})

reduce(model_results, full_join, by = "Term") %>%
  mutate(
    Mean_Estimate = rowMeans(select(., starts_with("Estimate")), na.rm = TRUE),
    Mean_SE = rowMeans(select(., starts_with("SE")), na.rm = TRUE),
    Mean_t_value = rowMeans(select(., starts_with("t_value")), na.rm = TRUE),
    Mean_p_value = rowMeans(select(., starts_with("p_value")), na.rm = TRUE)
  ) %>%
  select(Term, Mean_Estimate, Mean_SE, Mean_t_value, Mean_p_value)
```


#### With social anxiety
dmpfc - stateRatings X neuralSimCondition1
rtpj - neuralSimConditionCodes2 X saTotal
```{r}
# dmpfc 
model_results <- lapply(1:25, function(i) {
  model <- lmer(deconMeanCor ~
                  traitRatings +
                  stateRatings*neuralSimConditionCodes*saTotalC +
                  (1 | dyad),
                data = dmPFC_data[[i]])
  
  # Extract coefficients and p-values
  summary_data <- coef(summary(model))
  data.frame(
    Term = rownames(summary_data),
    Estimate = summary_data[, "Estimate"],
    SE = summary_data[, "Std. Error"],
    t_value = summary_data[, "t value"],
    p_value = summary_data[, "Pr(>|t|)"]
  )
})

reduce(model_results, full_join, by = "Term") %>%
  mutate(
    Mean_Estimate = rowMeans(select(., starts_with("Estimate")), na.rm = TRUE),
    Mean_SE = rowMeans(select(., starts_with("SE")), na.rm = TRUE),
    Mean_t_value = rowMeans(select(., starts_with("t_value")), na.rm = TRUE),
    Mean_p_value = rowMeans(select(., starts_with("p_value")), na.rm = TRUE)
  ) %>%
  select(Term, Mean_Estimate, Mean_SE, Mean_t_value, Mean_p_value)

# vmpfc
model_results <- lapply(1:25, function(i) {
  model <- lmer(deconMeanCor ~
                  traitRatings +
                  stateRatings*neuralSimConditionCodes*saTotalC +
                  (1 | dyad),
                data = vmPFC_data[[i]])
  
  # Extract coefficients and p-values
  summary_data <- coef(summary(model))
  data.frame(
    Term = rownames(summary_data),
    Estimate = summary_data[, "Estimate"],
    SE = summary_data[, "Std. Error"],
    t_value = summary_data[, "t value"],
    p_value = summary_data[, "Pr(>|t|)"]
  )
})

reduce(model_results, full_join, by = "Term") %>%
  mutate(
    Mean_Estimate = rowMeans(select(., starts_with("Estimate")), na.rm = TRUE),
    Mean_SE = rowMeans(select(., starts_with("SE")), na.rm = TRUE),
    Mean_t_value = rowMeans(select(., starts_with("t_value")), na.rm = TRUE),
    Mean_p_value = rowMeans(select(., starts_with("p_value")), na.rm = TRUE)
  ) %>%
  select(Term, Mean_Estimate, Mean_SE, Mean_t_value, Mean_p_value)

# rtpj - stateRatings:neuralSimConditionCodes1	0.0331999289	0.017428905	0.07470767
model_results <- lapply(1:25, function(i) {
  model <- lmer(deconMeanCor ~
                  traitRatings +
                  stateRatings*neuralSimConditionCodes*saTotalC +
                  (1 | dyad),
                data = rTPJ_data[[i]])
  
  # Extract coefficients and p-values
  summary_data <- coef(summary(model))
  data.frame(
    Term = rownames(summary_data),
    Estimate = summary_data[, "Estimate"],
    SE = summary_data[, "Std. Error"],
    t_value = summary_data[, "t value"],
    p_value = summary_data[, "Pr(>|t|)"]
  )
})

reduce(model_results, full_join, by = "Term") %>%
  mutate(
    Mean_Estimate = rowMeans(select(., starts_with("Estimate")), na.rm = TRUE),
    Mean_SE = rowMeans(select(., starts_with("SE")), na.rm = TRUE),
    Mean_t_value = rowMeans(select(., starts_with("t_value")), na.rm = TRUE),
    Mean_p_value = rowMeans(select(., starts_with("p_value")), na.rm = TRUE)
  ) %>%
  select(Term, Mean_Estimate, Mean_SE, Mean_t_value, Mean_p_value)

# ltpj
model_results <- lapply(1:25, function(i) {
  model <- lmer(deconMeanCor ~
                  traitRatings +
                  stateRatings*neuralSimConditionCodes*saTotalC +
                  (1 | dyad),
                data = lTPJ_data[[i]])
  
  # Extract coefficients and p-values
  summary_data <- coef(summary(model))
  data.frame(
    Term = rownames(summary_data),
    Estimate = summary_data[, "Estimate"],
    SE = summary_data[, "Std. Error"],
    t_value = summary_data[, "t value"],
    p_value = summary_data[, "Pr(>|t|)"]
  )
})

reduce(model_results, full_join, by = "Term") %>%
  mutate(
    Mean_Estimate = rowMeans(select(., starts_with("Estimate")), na.rm = TRUE),
    Mean_SE = rowMeans(select(., starts_with("SE")), na.rm = TRUE),
    Mean_t_value = rowMeans(select(., starts_with("t_value")), na.rm = TRUE),
    Mean_p_value = rowMeans(select(., starts_with("p_value")), na.rm = TRUE)
  ) %>%
  select(Term, Mean_Estimate, Mean_SE, Mean_t_value, Mean_p_value)
```


#### Plot region interactions
```{r}
# dmPFC
dmpfc_plot <- plot_model(dmpfc_model, type = "pred", 
           terms = c("stateRatings", "neuralSimConditionCodes")) +
  ggtitle("") + 
  labs(y = "Neural Similarity",
       x = "Affective Similarity",
       color = "Condition") +
  scale_color_manual(labels = c("Same-Stimuli", "Self-Perspective", "Friend-Perspective"), 
                     values = c("#287C8E", "#440154", "#8FD744"),
                     drop = FALSE) +
  scale_fill_manual(labels = c("Same-Stimuli", "Self-Perspective", "Friend-Perspective"), 
                    values = c("#287C8E", "#440154", "#8FD744"), 
                    drop = FALSE) +
  ggtitle("A - dmPFC")

# rTPJ
rtpj_plot <- plot_model(rtpj_model, type = "pred", 
           terms = c("saTotalC", "neuralSimConditionCodes")) +
  ggtitle("") + 
  labs(y = "Neural Similarity",
       x = "Social Anxiety Symptoms",
       color = "Condition") +
  scale_color_manual(labels = c("Same-Stimuli", "Self-Perspective", "Friend-Perspective"), 
                     values = c("#287C8E", "#440154", "#8FD744"),
                     drop = FALSE) +
  scale_fill_manual(labels = c("Same-Stimuli", "Self-Perspective", "Friend-Perspective"), 
                    values = c("#287C8E", "#440154", "#8FD744"), 
                    drop = FALSE) +
  ggtitle("B - rTPJ")

regions <- (dmpfc_plot | rtpj_plot) + plot_layout(guides = "collect")

ggsave("/Users/aliciavallorani/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Research Projects/F31/BFFs/analyses/neural_similarity/output/figures/regions.png", plot = regions, 
       width = 15, height = 6) 
```


#### Multiple regions
Effect is strongest when considering only dmPFC and rTPJ
```{r}
# dmpfc & rTPJ
model_results <- lapply(1:25, function(i) {
  model <- lmer(deconMeanCor ~
                  traitRatings +
                  stateRatings*neuralSimConditionCodes*saTotalC +
                  (1 | dyad),
                data = dmPFC_rTPJ_data[[i]])
  
  # Extract coefficients and p-values
  summary_data <- coef(summary(model))
  data.frame(
    Term = rownames(summary_data),
    Estimate = summary_data[, "Estimate"],
    SE = summary_data[, "Std. Error"],
    t_value = summary_data[, "t value"],
    p_value = summary_data[, "Pr(>|t|)"]
  )
})

reduce(model_results, full_join, by = "Term") %>%
  mutate(
    Mean_Estimate = rowMeans(select(., starts_with("Estimate")), na.rm = TRUE),
    Mean_SE = rowMeans(select(., starts_with("SE")), na.rm = TRUE),
    Mean_t_value = rowMeans(select(., starts_with("t_value")), na.rm = TRUE),
    Mean_p_value = rowMeans(select(., starts_with("p_value")), na.rm = TRUE)
  ) %>%
  select(Term, Mean_Estimate, Mean_SE, Mean_t_value, Mean_p_value)


# vmpfc & lTPJ
model_results <- lapply(1:25, function(i) {
  model <- lmer(deconMeanCor ~
                  traitRatings +
                  stateRatings*neuralSimConditionCodes*saTotalC +
                  (1 | dyad),
                data = vmPFC_lTPJ_data[[i]])
  
  # Extract coefficients and p-values
  summary_data <- coef(summary(model))
  data.frame(
    Term = rownames(summary_data),
    Estimate = summary_data[, "Estimate"],
    SE = summary_data[, "Std. Error"],
    t_value = summary_data[, "t value"],
    p_value = summary_data[, "Pr(>|t|)"]
  )
})

reduce(model_results, full_join, by = "Term") %>%
  mutate(
    Mean_Estimate = rowMeans(select(., starts_with("Estimate")), na.rm = TRUE),
    Mean_SE = rowMeans(select(., starts_with("SE")), na.rm = TRUE),
    Mean_t_value = rowMeans(select(., starts_with("t_value")), na.rm = TRUE),
    Mean_p_value = rowMeans(select(., starts_with("p_value")), na.rm = TRUE)
  ) %>%
  select(Term, Mean_Estimate, Mean_SE, Mean_t_value, Mean_p_value)

# dmpfc vmpfc & rtpj
model_results <- lapply(1:25, function(i) {
  model <- lmer(deconMeanCor ~
                  traitRatings +
                  stateRatings*neuralSimConditionCodes*saTotalC +
                  (1 | dyad),
                data = dmPFC_vmPFC_rTPJ_data[[i]])
  
  # Extract coefficients and p-values
  summary_data <- coef(summary(model))
  data.frame(
    Term = rownames(summary_data),
    Estimate = summary_data[, "Estimate"],
    SE = summary_data[, "Std. Error"],
    t_value = summary_data[, "t value"],
    p_value = summary_data[, "Pr(>|t|)"]
  )
})

reduce(model_results, full_join, by = "Term") %>%
  mutate(
    Mean_Estimate = rowMeans(select(., starts_with("Estimate")), na.rm = TRUE),
    Mean_SE = rowMeans(select(., starts_with("SE")), na.rm = TRUE),
    Mean_t_value = rowMeans(select(., starts_with("t_value")), na.rm = TRUE),
    Mean_p_value = rowMeans(select(., starts_with("p_value")), na.rm = TRUE)
  ) %>%
  select(Term, Mean_Estimate, Mean_SE, Mean_t_value, Mean_p_value)
```

