---
title: "bffs_neuralsim_analyses_12072023"
author: "Alicia Vallorani"
date: "2023-12-07"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if (!("pacman" %in% installed.packages()[,])) {
    install.packages("pacman")
  }
pacman::p_load(tidyverse, psych, Hmisc, mice, miceadds, lmerTest, broom.mixed, 
               sjPlot, viridis)

source("/Users/aliciavallorani/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Research Projects/Standard Codes/check_singularity.R")

source("/Users/aliciavallorani/Library/CloudStorage/Box-Box/Standard Codes/visualization_tools/basic_theme.R")
theme_set(basic_theme)

project_path <- "/Users/aliciavallorani/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Research Projects/F31/BFFs/analyses/neural_similarity" 

# QST data
qst_df <- read.csv(file.path(project_path,
                             "/data/for_analysis/bffs_questionnaires_01192024.csv", 
                             fsep = ""), stringsAsFactors = TRUE) |>
  # Adjust reported ethnicity
  mutate(ethnicity = recode(ethnicity, `Another ethnicity` = "Another ethnicity", 
                            `Hispanic/Latino/Latina/Latinx` = "Hispanic/Latino/Latina/Latinx", 
                            `Hispanic/Latino/Latina/Latinx, Non-Hispanic` =
                              "Hispanic/Latino/Latina/Latinx", 
                            `Non-Hispanic` = "Non-Hispanic", 
                            `Non-Hispanic, Unknown` = "Non-Hispanic",
                            `Unknown` = "Unknown"))

# Neural sim synchrony data
synchrony_df <- read.csv(file.path(project_path,
                             "/data/for_analysis/neural_similarity_data_synchrony_12092023.csv", 
                             fsep = ""), stringsAsFactors = FALSE) 

synchrony_df <- full_join(synchrony_df, qst_df) |>
  # Recode data
  mutate(neuralSimConditionAnalysis = ifelse(id %% 2 != 0 & neuralSimConditionSpecific == "odd_self_even_friend", "selfClassic", ifelse(id %% 2 == 0 & neuralSimConditionSpecific == "odd_self_even_friend", "friendClassic", ifelse(id %% 2 != 0 & neuralSimConditionSpecific == "even_self_odd_friend", "friendClassic", ifelse(id %% 2 == 0 & neuralSimConditionSpecific == "even_self_odd_friend", "selfClassic", ifelse(neuralSimConditionSpecific == "odd_self_even_self", "selfPerspective", ifelse(neuralSimConditionSpecific == "odd_friend_even_friend", "friendPerspective", NA)))))),
         neuralSimConditionCodes = as.factor(recode(neuralSimConditionAnalysis,
                                                    `selfClassic` = 0, 
                                                    `friendClassic` = 1,
                                                    `selfPerspective` = 2,
                                                    `friendPerspective` = 3)),
         atlasNameCodes = as.factor(recode(atlasName, `dmPFC` = 0, `vmPFC` = 1,
                                           `rTPJ` = 2, `lTPJ` = 3))) |>
  # Disambigulate within and between variance
  group_by(dyad) |>
  mutate(traitRatings = mean(ratingSynchrony, na.rm = TRUE),
         stateRatings = ratingSynchrony - traitRatings) |>
  ungroup() |>
  mutate_all(~ifelse(is.nan(.), NA, .)) |>
  select(dyad, id, saTotal, atlasName, atlasNameCodes, clips, ratingSynchrony, 
         traitRatings, stateRatings, neuralSimCondition, neuralSimConditionAnalysis, 
         neuralSimConditionCodes, neuralSimIntraClassCorrelation,
         siOverallVisit1, siOverallVisit2, raRespondentAffection, 
         uncomfortableWatchingSelf) |>
  mutate(neuralSimConditionCodes = as.factor(neuralSimConditionCodes),
        atlasNameCodes = as.factor(atlasNameCodes))

synchrony_df_na <- synchrony_df |> filter(!is.na(neuralSimIntraClassCorrelation)) |>
   mutate(stateRatingsC = as.numeric(scale(stateRatings, center = TRUE, scale = FALSE)),
          saTotalC = as.numeric(scale(saTotal, center = TRUE, scale = FALSE)))

included_ids <- synchrony_df_na |>
  select(dyad, id) |>
  unique() |>
  left_join(qst_df)
```


# BFFs Neural Similarity Analyses

## Demographics full sample
```{r}
# Handedness
## 1 = Left; 2 = Right
qst_df |>
  group_by(handedness) |>
  summarise(n())

# Race
## 1 = Another race; 2 = Asian; 3 = Black; 4 = White; 5 = Mixed 
qst_df |>
  group_by(race) |>
  summarise(n())

# Ethnicity
## 1 = Another ethnicity; 2 = Hispanic/Latino/Latina/Latinx; 3 = Non-Hispanic; 
## 4 = Unknown
qst_df |>
  group_by(ethnicity) |>
  summarise(n())

# Sex Assigned
## 1 = Assigned female; 2 = Assigned male
qst_df |>
  group_by(sexAssigned) |>
  summarise(n())

# Gender Identity
## 1 = Man; 2 = Woman; 3 = Chose not to identify
qst_df |>
  group_by(genderIdentity) |>
  summarise(n())

# Sexual Identity
## 1 = Another identity; 2 = Bisexual; 3 = Heterosexual; 4 = Lesbian/Gay; 
## 5 = Chose not to identify
qst_df |>
  group_by(sexualIdentity) |>
  summarise(n())
```


## Demographics partial sample
```{r}
# Handedness
## 1 = Left; 2 = Right
included_ids |>
  group_by(handedness) |>
  summarise(n())

# Race
## 1 = Another race; 2 = Asian; 3 = Black; 4 = White; 5 = Mixed 
included_ids |>
  group_by(race) |>
  summarise(n())

# Ethnicity
## 1 = Another ethnicity; 2 = Hispanic/Latino/Latina/Latinx; 3 = Non-Hispanic; 
## 4 = Unknown
included_ids |>
  group_by(ethnicity) |>
  summarise(n())

# Sex Assigned
## 1 = Assigned female; 2 = Assigned male
included_ids |>
  group_by(sexAssigned) |>
  summarise(n())

# Gender Identity
## 1 = Man; 2 = Woman; 3 = Chose not to identify
included_ids |>
  group_by(genderIdentity) |>
  summarise(n())

# Sexual Identity
## 1 = Another identity; 2 = Bisexual; 3 = Heterosexual; 4 = Lesbian/Gay; 
## 5 = Chose not to identify
included_ids |>
  group_by(sexualIdentity) |>
  summarise(n())
```

## Sample description
```{r}
# Full sample
psych::describe(qst_df |> select(ageVisit1, ageVisit2, weeksBetweenVisits,
                                 romAttract, sexAttract))

# Partial sample
psych::describe(included_ids |> select(ageVisit1, ageVisit2, weeksBetweenVisits,
                                       romAttract, sexAttract))

# Social anxiety distribution
psych::describe(included_ids$saTotal)

dist <- ggplot(included_ids, aes(saTotal)) +
  geom_histogram()
```


## Descriptives and correlations for between subjects measures
```{r}
# Describe
psych::describe(included_ids |> select(saTotal, siOverallVisit1, siOverallVisit2,
                                       raRespondentAffection, 
                                       uncomfortableWatchingSelf))

# Correlate 
rcorr(as.matrix(included_ids |> select(saTotal, siOverallVisit1, siOverallVisit2,
                                       raRespondentAffection, 
                                       uncomfortableWatchingSelf), type = "spearman"))

# Distribution of Social Anxiety Scores
dist <- ggplot(included_ids, aes(saTotal)) +
  geom_dotplot(binwidth = 8, dotsize = .9) +
  scale_x_continuous(breaks=seq(10, 90, 10), limits=c(10, 90)) +
  scale_y_continuous(NULL, breaks = NULL) +
  geom_vline(xintercept = 60) +
  labs(x = "Social Anxiety Symptoms")

ggsave("/Users/aliciavallorani/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Research Projects/F31/BFFs/analyses/neural_similarity/output/figures/dist.png", plot = dist, 
       width = 10, height = 6)
```


## Multilevel multiple imputation
```{r}
ini <- mice(synchrony_df_na, maxit = 0)
pred <- ini$pred
imputed_df <- mice(synchrony_df_na, m = 25, maxit = 50, method = 'pmm', seed = 500, pred=pred)
```


## Multilevel models
### Shared affect and social anxiety
Increasing state values = more agreement than average
```{r}
options(digits = 5, scipen = 999)
# Listwise delete
## Without SA
mlm1s <- with(synchrony_df_na, lmer(neuralSimIntraClassCorrelation ~
                                    uncomfortableWatchingSelf +
                                    siOverallVisit1 +
                                    siOverallVisit2 +
                                    raRespondentAffection +
                                    traitRatings + atlasNameCodes +
                                    stateRatings*neuralSimConditionCodes +
                                    (stateRatings|dyad)))
summary(mlm1s)

## With SA
mlm2s <- with(synchrony_df_na, lmer(neuralSimIntraClassCorrelation ~
                                    uncomfortableWatchingSelf +
                                    siOverallVisit1 +
                                    siOverallVisit2 +
                                    raRespondentAffection +
                                    traitRatings + atlasNameCodes +
                                    stateRatingsC*neuralSimConditionCodes*saTotalC +
                                    (stateRatings|dyad)))

summary(mlm2s)

## With SA - no control variables
mlm3s <- with(synchrony_df_na, lmer(neuralSimIntraClassCorrelation ~
                                    traitRatings + atlasNameCodes +
                                    stateRatingsC*neuralSimConditionCodes*saTotalC +
                                    (stateRatings|dyad)))

summary(mlm3s)


# Imputation
mlm1i <- with(imputed_df, lmer(neuralSimIntraClassCorrelation ~
                               uncomfortableWatchingSelf +
                               siOverallVisit1 +
                               siOverallVisit2 +
                               raRespondentAffection +
                               traitRatings + atlasNameCodes +
                               stateRatings*neuralSimConditionCodes +
                               (stateRatings|dyad)))

summary(est<- pool(mlm1i))

mlm2i <- with(imputed_df, lmer(neuralSimIntraClassCorrelation ~
                               uncomfortableWatchingSelf +
                               siOverallVisit1 +
                               siOverallVisit2 +
                               raRespondentAffection +
                               traitRatings + atlasNameCodes +
                               stateRatingsC*neuralSimConditionCodes*saTotalC +
                               (stateRatings|dyad)))

summary(est <- pool(mlm2i))
```


#### Create pooled random effects
```{r}
imp_list_df <- map(1:25, function(x) complete(imputed_df, x))

random_effects_list <- lapply(1:25, function(i) {
  model <- lmer(neuralSimIntraClassCorrelation ~
                uncomfortableWatchingSelf +
                siOverallVisit1 +
                siOverallVisit2 +
                raRespondentAffection +
                traitRatings + atlasNameCodes +
                stateRatingsC*neuralSimConditionCodes*saTotalC +
                (stateRatings|dyad),
                data = imp_list_df[[i]])
  
  # Extract the random effects information and return as a data frame
  data.frame(model = i, as.data.frame(summary(model)$varcor))
})

# Bind the list of data frames into a single data frame
combined_df <- bind_rows(random_effects_list) |>
  unite(item, c("grp", "var1", "var2")) |>
  mutate(item = str_replace_all(item, fixed("NA"), ""),
         item = str_replace_all(item, fixed("("), ""),
         item = str_replace_all(item, fixed(")"), ""),
         item = str_replace_all(item, fixed("_"), ""))

# Group by variable and calculate the mean for each variable
combined_df |>
  group_by(item) |>
  mutate(vcov_mean = mean(vcov),
         sdcor_mean = mean(sdcor)) |>
  select(item, vcov_mean, sdcor_mean) |>
  unique()
```


#### Run model across datasets separately to assess convergence warning
Based on outputs, singular convergence issue (dataset 6) is likely false positive.
```{r}
imp_list_df <- map(1:25, function(x) complete(imputed_df, x))

lapply(1:25, function(i) {
  model <- with(imp_list_df[[i]], lmer(neuralSimIntraClassCorrelation ~
                                       uncomfortableWatchingSelf +
                                       siOverallVisit1 +
                                       siOverallVisit2 +
                                       raRespondentAffection +
                                       traitRatings + atlasNameCodes +
                                       stateRatingsC*neuralSimConditionCodes*saTotalC +
                (stateRatings|dyad)))
  summary(model)
})
```


#### Plot interactions
```{r}
# Interaction between shared affect and perspective
int1 <- plot_model(mlm1s, type = "pred", 
           terms = c("stateRatings", "neuralSimConditionCodes")) +
  ggtitle("") + 
  labs(y = "Neural Similarity",
       x = "Shared Affect",
       color = "Condition") +
  scale_color_manual(labels = c("Self Classic", "Friend Classic",
                                "Self Perspective", "Friend Perspective"), 
                     values = c("#287C8E", "#404688", "#440154", "#8FD744"), 
                     drop = FALSE) +
  scale_fill_manual(labels = c("Self Classic", "Friend Classic",
                                "Self Perspective", "Friend Perspective"), 
                    values = c("#287C8E", "#404688", "#440154", "#8FD744"), 
                    drop = FALSE)

ggsave("/Users/aliciavallorani/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Research Projects/F31/BFFs/analyses/neural_similarity/output/figures/int1.png", plot = int1, 
       width = 10, height = 6) 


# Interaction between shared affect, perspective and social anxiety symptoms
int2 <- plot_model(mlm2s, type = "pred", 
           terms = c("stateRatingsC", "neuralSimConditionCodes", "saTotalC")) +
  ggtitle("") + 
  labs(y = "Neural Similarity",
       x = "Shared Affect",
       color = "Condition") +
  scale_color_manual(labels = c("Self Classic", "Friend Classic",
                                "Self Perspective", "Friend Perspective"), 
                     values = c("#287C8E", "#404688", "#440154", "#8FD744"), 
                     drop = FALSE) +
  scale_fill_manual(labels = c("Self Classic", "Friend Classic",
                                "Self Perspective", "Friend Perspective"), 
                    values = c("#287C8E", "#404688", "#440154", "#8FD744"), 
                    drop = FALSE)

int2$data$facet <- ifelse(int2$data$facet == "saTotalC = -20.32", 
                          "Social Anxiety = 28.53",
                          ifelse(int2$data$facet == "saTotalC = -0.84",
                                 "Social Anxiety = 48.01",
                                 ifelse(int2$data$facet == "saTotalC = 18.63",
                                        "Social Anxiety = 67.48", NA)))


ggsave("/Users/aliciavallorani/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Research Projects/F31/BFFs/analyses/neural_similarity/output/figures/int2.png", plot = int2, 
       width = 10, height = 6)
```

### Mentalizing region and perspective
```{r}
mlm3i <- with(imputed_df, lmer(neuralSimIntraClassCorrelation ~
                               uncomfortableWatchingSelf +
                               siOverallVisit1 +
                               siOverallVisit2 +
                               raRespondentAffection +
                               atlasNameCodes*neuralSimConditionCodes +
                               (1|dyad)))

summary(est<- pool(mlm3i))
```


#### Create pooled random effects
```{r}
random_effects_list2 <- lapply(1:25, function(i) {
  model <- lmer(neuralSimIntraClassCorrelation ~
                uncomfortableWatchingSelf +
                siOverallVisit1 +
                siOverallVisit2 +
                raRespondentAffection +
                atlasNameCodes*neuralSimConditionCodes +
                (1|dyad),
                data = imp_list_df[[i]])
  
  # Extract the random effects information and return as a data frame
  data.frame(model = i, as.data.frame(summary(model)$varcor))
})

# Bind the list of data frames into a single data frame
combined_df2 <- bind_rows(random_effects_list2) |>
  unite(item, c("grp", "var1", "var2")) |>
  mutate(item = str_replace_all(item, fixed("NA"), ""),
         item = str_replace_all(item, fixed("("), ""),
         item = str_replace_all(item, fixed(")"), ""),
         item = str_replace_all(item, fixed("_"), ""))

# Group by variable and calculate the mean for each variable
combined_df2 |>
  group_by(item) |>
  mutate(vcov_mean = mean(vcov),
         sdcor_mean = mean(sdcor)) |>
  select(item, vcov_mean, sdcor_mean) |>
  unique()
```