---
title: "bffs_neuralsim_cleaning_11282023"
author: "Alicia Vallorani"
date: "2023-11-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if (!("pacman" %in% installed.packages()[,])) {
    install.packages("pacman")
  }
pacman::p_load(tidyverse, fs, irr, broom)

project_path <- "/Users/aliciavallorani/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Research Projects/F31/BFFs/analyses/neural_similarity" 

source("/Users/aliciavallorani/Library/CloudStorage/Box-Box/Standard Codes/visualization_tools/basic_theme.R")
theme_set(basic_theme)

# File paths
self_path <- file.path(project_path,"/data/for_prep/self_deconvolution_11142023/deconvolved/self_aligned_11202023", fsep = "")

friend_path <- file.path(project_path,"/data/for_prep/friend_deconvolution_11142023/deconvolved/friend_aligned_11202023", fsep = "")

# For exporting figures
out_path <- file.path(project_path,"/data/for_analysis", fsep = "")
```


# fMRI data
## Self data
```{r}
# Read in the data
self_files <- dir_ls(self_path, regexp = "\\.csv.gz$")
self_data <- self_files |>
  map_dfr(read_csv, .id = "id") |>
  mutate(id = str_sub(id, start = 218, end = -33),
         id = paste0(substr(id, 1, 4), "_", 
                     substr(id, 5, 6), "_", 
                     substr(id, 7, 8)),
         atlasName = recode(atlas_value, 
                            `1` = "dmPFC", 
                            `2` = "rTPJ",
                            `4` = "lTPJ", 
                            `5` = "precuneus",
                            `7` = "vmPFC",
                            `8` = "cerebellum1",
                            `10` = "cerebellum2",
                            `13` = "POS1")) |> # parieto‐occipital sulcus
  filter(evt_time >= 0) |>
  group_by(id, trial, atlasName) |>
  mutate(time = seq_along(evt_time)) |>
  ungroup() |>
  rename(deconMean = decon_mean) |>
  select(id, atlasName, trial, time, deconMean)

# Read in trial info
self_trials <- read.csv("/Users/aliciavallorani/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Research Projects/F31/BFFs/data_collection/fmri_task_data/output/bffs_self_trialdata_09252023.csv") |>
  rename(runName = run_name) |>
  select(id, runName, trial, clips) 

# Merge data
self <- left_join(self_data, self_trials) |>
  separate(id, c("study", "dyad", "id")) |>
  mutate(dyad = as.numeric(dyad),
         id = as.numeric(id)) |>
  select(-study) |>
  # Mistake where 23372243 has extra trials that don't exist
  filter(trial <= 18)
```


## Friend data
```{r}
# Read in the data
friend_files <- dir_ls(friend_path, regexp = "\\.csv.gz$")
friend_data <- friend_files |>
  map_dfr(read_csv, .id = "id") |>
  mutate(id = str_sub(id, start = 222, end = -33),
         id = paste0(substr(id, 1, 4), "_", 
                     substr(id, 5, 6), "_", 
                     substr(id, 7, 8)),
         atlasName = recode(atlas_value, 
                            `1` = "dmPFC", 
                            `2` = "rTPJ",
                            `4` = "lTPJ", 
                            `5` = "precuneus",
                            `7` = "vmPFC",
                            `8` = "cerebellum1",
                            `10` = "cerebellum2",
                            `13` = "POS1")) |> # parieto‐occipital sulcus
  filter(evt_time >= 0) |>
  group_by(id, trial, atlasName) |>
  mutate(time = seq_along(evt_time)) |>
  ungroup() |>
  rename(deconMean = decon_mean) |>
  select(id, atlasName, trial, time, deconMean)

# Read in trial info
friend_trials <- read.csv("/Users/aliciavallorani/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Research Projects/F31/BFFs/data_collection/fmri_task_data/output/bffs_friend_trialdata_09252023.csv") |>
  rename(runName = run_name) |>
  select(id, runName, trial, clips)

# Merge data
friend <- left_join(friend_data, friend_trials) |>
  separate(id, c("study", "dyad", "id")) |>
  mutate(dyad = as.numeric(dyad),
         id = as.numeric(id)) |>
  select(-study)
```


## Classic neural similarity (same videos)
For each person in the dyad their self run matches their partner's friend run.
```{r}
# ICC where odd is self and even is friend
## Separate data.frames
odd_participants_self_1 <- self |>
  filter(id %% 2 != 0) 

even_participants_friend_1 <- friend |>
  filter(id %% 2 == 0) 

## Rejoin data.frames
cns_oself_efriend <- full_join(odd_participants_self_1,
                               even_participants_friend_1) |>
  filter(atlasName == "dmPFC" | atlasName == "vmPFC" |
         atlasName == "rTPJ"  | atlasName == "lTPJ")

## Split data.frames
cns_oself_efriend_list <- split(cns_oself_efriend, 
                                cns_oself_efriend[c("dyad", "atlasName", 
                                                    "clips")])
## Pivot data.frames for calculation
cns_oself_efriend_list <- lapply(cns_oself_efriend_list, function(tibble) {
  as.data.frame(select(tibble, id, deconMean)) |>
  group_by(id) |>
  mutate(row = seq_along(id)) |>
  pivot_wider(names_from = id, values_from = deconMean) |>
  select(-row)
})

## Calculate ICC
df_names <- names(cns_oself_efriend_list)
icc_values <- numeric(length(df_names))

for (i in seq_along(df_names)) {
  df_name <- df_names[i]

  icc_call <- paste0("icc(cns_oself_efriend_list[['", df_name, "']], model = 'twoway', type = 'agreement')")

  icc_result <- eval(parse(text = icc_call))
  
  icc_values[i] <- icc_result$value
}

## Finalize data.frame
cns_oself_efriend_icc <- data.frame(df_name = df_names, icc_value = icc_values) |>
  separate(df_name, c("dyad", "atlasName", "clips")) |>
  mutate(neuralSimCondition = "classic",
         neuralSimConditionSpecific = "odd_self_even_friend") |>
  rename(neuralSimIntraClassCorrelation = icc_value)



# ICC where even is self and odd is friend
## Separate data.frames
odd_participants_friend_1 <- friend |>
  filter(id %% 2 != 0) 

even_participants_self_1 <- self |>
  filter(id %% 2 == 0) 

## Rejoin data.frames
cns_eself_ofriend <- full_join(odd_participants_friend_1,
                               even_participants_self_1) |>
  filter(atlasName == "dmPFC" | atlasName == "vmPFC" |
         atlasName == "rTPJ"  | atlasName == "lTPJ")

## Split data.frames
cns_eself_ofriend_list <- split(cns_eself_ofriend, 
                                cns_eself_ofriend[c("dyad", "atlasName", 
                                                    "clips")])
## Pivot data.frames for calculation
cns_eself_ofriend_list <- lapply(cns_eself_ofriend_list, function(tibble) {
  as.data.frame(select(tibble, id, deconMean)) |>
  group_by(id) |>
  mutate(row = seq_along(id)) |>
  pivot_wider(names_from = id, values_from = deconMean) |>
  select(-row)
})

## Calculate ICC
df_names <- names(cns_eself_ofriend_list)
icc_values <- numeric(length(df_names))

for (i in seq_along(df_names)) {
  df_name <- df_names[i]

  icc_call <- paste0("icc(cns_eself_ofriend_list[['", df_name, "']], model = 'twoway', type = 'agreement')")

  icc_result <- eval(parse(text = icc_call))
  
  icc_values[i] <- icc_result$value
}

## Finalize data.frame
cns_eself_ofriend_icc <- data.frame(df_name = df_names, icc_value = icc_values) |>
  separate(df_name, c("dyad", "atlasName", "clips")) |>
  mutate(neuralSimCondition = "classic",
         neuralSimConditionSpecific = "even_self_odd_friend") |>
  rename(neuralSimIntraClassCorrelation = icc_value)
```


## Perspective neural similarity (opposite video same moment)
For each person in the dyad, their self run matches their friend's self run and
their friend run matches their friend's friend run
```{r}
# ICC where odd is self and even is self
## Rejoin data.frames
cns_oself_eself <- full_join(odd_participants_self_1,
                             even_participants_self_1) |>
  filter(atlasName == "dmPFC" | atlasName == "vmPFC" |
         atlasName == "rTPJ"  | atlasName == "lTPJ")

## Split data.frames
cns_oself_eself_list <- split(cns_oself_eself, cns_oself_eself[c("dyad", 
                                                                 "atlasName", 
                                                                 "clips")])
## Pivot data.frames for calculation
cns_oself_eself_list <- lapply(cns_oself_eself_list, function(tibble) {
  as.data.frame(select(tibble, id, deconMean)) |>
  group_by(id) |>
  mutate(row = seq_along(id)) |>
  pivot_wider(names_from = id, values_from = deconMean) |>
  select(-row)
})

## Calculate ICC
df_names <- names(cns_oself_eself_list)
icc_values <- numeric(length(df_names))

for (i in seq_along(df_names)) {
  df_name <- df_names[i]

  icc_call <- paste0("icc(cns_oself_eself_list[['", df_name, "']], model = 'twoway', type = 'agreement')")

  icc_result <- eval(parse(text = icc_call))
  
  icc_values[i] <- icc_result$value
}

## Finalize data.frame
cns_oself_eself_icc <- data.frame(df_name = df_names, icc_value = icc_values) |>
  separate(df_name, c("dyad", "atlasName", "clips")) |>
  mutate(neuralSimCondition = "perspective",
         neuralSimConditionSpecific = "odd_self_even_self") |>
  rename(neuralSimIntraClassCorrelation = icc_value)



# ICC where even is friend and odd is friend
## Rejoin data.frames
cns_efriend_ofriend <- full_join(odd_participants_friend_1,
                                 even_participants_friend_1) |>
  filter(atlasName == "dmPFC" | atlasName == "vmPFC" |
         atlasName == "rTPJ"  | atlasName == "lTPJ")

## Split data.frames
cns_efriend_ofriend_list <- split(cns_efriend_ofriend, 
                                  cns_efriend_ofriend[c("dyad", "atlasName", 
                                                        "clips")])
## Pivot data.frames for calculation
cns_efriend_ofriend_list <- lapply(cns_efriend_ofriend_list, function(tibble) {
  as.data.frame(select(tibble, id, deconMean)) |>
  group_by(id) |>
  mutate(row = seq_along(id)) |>
  pivot_wider(names_from = id, values_from = deconMean) |>
  select(-row)
})

## Calculate ICC
df_names <- names(cns_efriend_ofriend_list)
icc_values <- numeric(length(df_names))

for (i in seq_along(df_names)) {
  df_name <- df_names[i]

  icc_call <- paste0("icc(cns_efriend_ofriend_list[['", df_name, "']], model = 'twoway', type = 'agreement')")

  icc_result <- eval(parse(text = icc_call))
  
  icc_values[i] <- icc_result$value
}

## Finalize data.frame
cns_efriend_ofriend_icc <- data.frame(df_name = df_names, icc_value = icc_values) |>
  separate(df_name, c("dyad", "atlasName", "clips")) |>
  mutate(neuralSimCondition = "perspective",
         neuralSimConditionSpecific = "odd_friend_even_friend") |>
  rename(neuralSimIntraClassCorrelation = icc_value)
```


## Merge neural similarity data
```{r}
neural_similarity_data <- Reduce(function(...) {full_join(...)}, 
                                 list(cns_oself_efriend_icc, 
                                      cns_eself_ofriend_icc,
                                      cns_oself_eself_icc,
                                      cns_efriend_ofriend_icc)) |>
  mutate(dyad = as.numeric(dyad))
```


# Participant responses in scanner
## Self data
```{r}
self_dir <- "/Users/aliciavallorani/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Research Projects/F31/BFFs/data_collection/fmri_task_data/self"
self_files <- dir_ls(self_dir, regexp = "\\.csv$")

self_df_tri <- self_files |>
  map_dfr(read_csv, col_types = list(pos_resp.keys = col_double(),
                                     neg_resp.keys = col_double(),
                                     participant = col_double(),
                                     dyad = col_double())) |>
  mutate(id = substr(clips, 29, 38),
         clips = substr(clips, 40, 43)) |>
  select(id, clips, pos_resp.keys, neg_resp.keys, run1.thisTrialN) |>
  rename(feltPositive = pos_resp.keys,
         feltNegative = neg_resp.keys,
         trial = run1.thisTrialN) |>
  filter(id == "2337_02_03" | id == "2337_02_04" | id == "2337_03_05" |
         id == "2337_03_06" | id == "2337_04_07" | id == "2337_05_10" |
         id == "2337_07_13" | id == "2337_07_14" | id == "2337_08_15" |
         id == "2337_08_16" | id == "2337_09_17" | id == "2337_10_19" | 
         id == "2337_11_21" | id == "2337_11_22" | id == "2337_12_23" |
         id == "2337_12_24" | id == "2337_13_25" | id == "2337_13_26" |
         id == "2337_14_27" | id == "2337_14_28" | id == "2337_15_29" |
         id == "2337_15_30" | id == "2337_16_31" | id == "2337_16_32" |
         id == "2337_19_37" | id == "2337_20_39" | id == "2337_22_43" |
         id == "2337_22_44" | id == "2337_23_45" | id == "2337_23_46" |
         id == "2337_24_48" | id == "2337_27_54" | id == "2337_30_59" |
         id == "2337_30_60" | id == "2337_32_63" | id == "2337_32_64" |
         id == "2337_33_65" | id == "2337_34_67" | id == "2337_34_68" |
         id == "2337_35_69" | id == "2337_35_70" | id == "2337_37_73" |
         id == "2337_37_74") |>
  # Recode left had response values
  mutate(feltPositive = ifelse(feltPositive == 9, 1,
                               ifelse(feltPositive == 8, 2,
                                      ifelse(feltPositive == 7, 3,
                                             ifelse(feltPositive == 6, 4,
                                                    feltPositive)))),
         feltNegative = ifelse(feltNegative == 9, 1,
                               ifelse(feltNegative == 8, 2,
                                      ifelse(feltNegative == 7, 3,
                                             ifelse(feltNegative == 6, 4,
                                                    feltNegative))))) |>
  separate(id, c("study", "dyad", "id")) |>
  mutate(dyad = as.numeric(dyad),
         id = as.numeric(id),
         feltPositive = recode(feltPositive, `1` = 5, `2` = 6, 
                                             `3` = 7, `4` = 8),
         # Higher scores represent more positive affect
         feltPositiveMinusNegative = feltPositive - feltNegative,
         trial = recode(trial, `0` = 1, `1` = 2, `2` = 3, `3` = 4, `4` = 5,
                               `5` = 6, `6` = 7, `7` = 8, `8` = 9, `9` = 10,
                               `10` = 11, `11` = 12, `12` = 13, `13` = 14,
                               `14` = 15, `15` = 16, `16` = 17, `17` = 18)) |>
  select(-study) 
```


## Friend data
```{r}
friend_dir <- "/Users/aliciavallorani/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Research Projects/F31/BFFs/data_collection/fmri_task_data/friend"
friend_files <- dir_ls(friend_dir, regexp = "\\.csv$")

friend_df_tri <- friend_files |> 
  map_dfr(read_csv,  .id = "id", col_types = list(pos_resp.keys = col_double(),
                                                  neg_resp.keys = col_double(),
                                                  participant = col_double(),
                                                  dyad = col_double(),
                                                  frameRate = col_double())) |>
  mutate(id = substr(id, 150, 159),
         clips = substr(clips, 40, 43)) |>
  select(id, clips, pos_resp.keys, neg_resp.keys, run2.thisTrialN) |>
  rename(feltPositive = pos_resp.keys,
         feltNegative = neg_resp.keys,
         trial = run2.thisTrialN) |>
  filter(id == "2337_02_03" | id == "2337_02_04" | id == "2337_03_05" |
         id == "2337_03_06" | id == "2337_04_07" | id == "2337_05_10" |
         id == "2337_07_13" | id == "2337_07_14" | id == "2337_08_15" |
         id == "2337_08_16" | id == "2337_09_17" | id == "2337_10_19" | 
         id == "2337_11_21" | id == "2337_11_22" | id == "2337_12_23" |
         id == "2337_12_24" | id == "2337_13_25" | id == "2337_13_26" |
         id == "2337_14_27" | id == "2337_14_28" | id == "2337_15_29" |
         id == "2337_15_30" | id == "2337_16_31" | id == "2337_16_32" |
         id == "2337_19_37" | id == "2337_20_39" | id == "2337_22_43" |
         id == "2337_22_44" | id == "2337_23_45" | id == "2337_23_46" |
         id == "2337_24_48" | id == "2337_27_54" | id == "2337_30_59" |
         id == "2337_30_60" | id == "2337_32_63" | id == "2337_32_64" |
         id == "2337_33_66" | id == "2337_34_67" | id == "2337_34_68" |
         id == "2337_35_69" | id == "2337_35_70" | id == "2337_37_73" |
         id == "2337_37_74" | id == "2337_05_09") |>
  # Recode left had response values
  mutate(feltPositive = ifelse(feltPositive == 9, 1,
                               ifelse(feltPositive == 8, 2,
                                      ifelse(feltPositive == 7, 3,
                                             ifelse(feltPositive == 6, 4,
                                                    feltPositive)))),
         feltNegative = ifelse(feltNegative == 9, 1,
                               ifelse(feltNegative == 8, 2,
                                      ifelse(feltNegative == 7, 3,
                                             ifelse(feltNegative == 6, 4,
                                                    feltNegative))))) |>
  separate(id, c("study", "dyad", "id")) |>
  mutate(dyad = as.numeric(dyad),
         id = as.numeric(id),
         run = "friend",
         feltPositive = recode(feltPositive, `1` = 5, `2` = 6, 
                                             `3` = 7, `4` = 8),
         # Higher scores represent more positive affect
         feltPositiveMinusNegative = feltPositive - feltNegative,
         trial = recode(trial, `0` = 1, `1` = 2, `2` = 3, `3` = 4, `4` = 5,
                               `5` = 6, `6` = 7, `7` = 8, `8` = 9, `9` = 10,
                               `10` = 11, `11` = 12, `12` = 13, `13` = 14,
                               `14` = 15, `15` = 16, `16` = 17, `17` = 18)) |>
  select(-study) |>
  filter(!is.na(trial))
```


## Classic neural similarity ratings
```{r}
# First merge
odd_participants_self_ratings_1 <- self_df_tri |>
  filter(id %% 2 != 0) |>
  select(dyad, id, trial, clips, feltPositiveMinusNegative) 

even_participants_friend_ratings_1 <- friend_df_tri |>
  filter(id %% 2 == 0) |>
  select(dyad, id, trial, clips, feltPositiveMinusNegative) 

classic_neural_similarity_ratings_1 <- full_join(odd_participants_self_ratings_1,
                                                 even_participants_friend_ratings_1) |>
  mutate(neuralSimCondition = "classic",
         neuralSimConditionSpecific = "odd_self_even_friend") |>
  select(dyad, id, trial, clips, everything())
  
# Second merge
even_participants_self_ratings_1 <- self_df_tri |>
  filter(id %% 2 == 0) |>
  select(dyad, id, trial, clips, feltPositiveMinusNegative) 

odd_participants_friend_ratings_1 <- friend_df_tri |>
  filter(id %% 2 != 0)  |>
  select(dyad, id, trial, clips, feltPositiveMinusNegative) 

classic_neural_similarity_ratings_2 <- full_join(even_participants_self_ratings_1,
                                                 odd_participants_friend_ratings_1) |>
  mutate(neuralSimCondition = "classic",
         neuralSimConditionSpecific = "even_self_odd_friend") 

# Final merge
classic_neural_similarity_ratings <- full_join(classic_neural_similarity_ratings_1,
                                               classic_neural_similarity_ratings_2) 

classic_neural_similarity_ratings_odd <- classic_neural_similarity_ratings |>
  filter(id %% 2 != 0) |>
  rename(idOdd = id, trialOdd = trial, 
         feltPositiveMinusNegativeOdd = feltPositiveMinusNegative)

classic_neural_similarity_ratings_even <- classic_neural_similarity_ratings |>
  filter(id %% 2 == 0) |>
  rename(idEven = id, trialEven = trial, 
         feltPositiveMinusNegativeEven = feltPositiveMinusNegative)

classic_neural_similarity_ratings <- full_join(classic_neural_similarity_ratings_odd,
                                               classic_neural_similarity_ratings_even) |>
  select(dyad, idOdd, idEven, trialOdd, trialEven, clips, neuralSimCondition,
         neuralSimConditionSpecific, feltPositiveMinusNegativeOdd, feltPositiveMinusNegativeEven) |>
  mutate(ratingSynchrony = abs(feltPositiveMinusNegativeOdd - feltPositiveMinusNegativeEven)*-1)
```


## Perspective neural similarty ratings
```{r}
# First merge
odd_participants_self_ratings_2 <- self_df_tri |>
  filter(id %% 2 != 0) |>
  select(dyad, id, trial, clips, feltPositiveMinusNegative) 

even_participants_self_ratings_2 <- self_df_tri |>
  filter(id %% 2 == 0) |>
  select(dyad, id, trial, clips, feltPositiveMinusNegative)

perspective_neural_similarity_ratings_1 <- full_join(odd_participants_self_ratings_2,
                                                     even_participants_self_ratings_2) |>
  mutate(neuralSimCondition = "perspective",
         neuralSimConditionSpecific = "odd_self_even_self") 

# Second merge
odd_participants_friend_ratings_2 <- friend_df_tri |>
  filter(id %% 2 != 0) |>
  select(dyad, id, trial, clips, feltPositiveMinusNegative) 

even_participants_friend_ratings_2 <- friend_df_tri |>
  filter(id %% 2 == 0) |>
  select(dyad, id, trial, clips, feltPositiveMinusNegative) 

perspective_neural_similarity_ratings_2 <- full_join(odd_participants_friend_ratings_2,
                                                     even_participants_friend_ratings_2) |>
  mutate(neuralSimCondition = "perspective",
         neuralSimConditionSpecific = "odd_friend_even_friend") 

# Final merge
perspective_neural_similarity_ratings <- full_join(perspective_neural_similarity_ratings_1,
                                                   perspective_neural_similarity_ratings_2) 

perspective_neural_similarity_ratings_odd <- perspective_neural_similarity_ratings |>
  filter(id %% 2 != 0) |>
  rename(idOdd = id, trialOdd = trial, 
         feltPositiveMinusNegativeOdd = feltPositiveMinusNegative)

perspective_neural_similarity_ratings_even <- perspective_neural_similarity_ratings |>
  filter(id %% 2 == 0) |>
  rename(idEven = id, trialEven = trial, 
         feltPositiveMinusNegativeEven = feltPositiveMinusNegative)

perspective_neural_similarity_ratings <- full_join(perspective_neural_similarity_ratings_odd,
                                                   perspective_neural_similarity_ratings_even) |>
  select(dyad, idOdd, idEven, trialOdd, trialEven, clips, neuralSimCondition,
         neuralSimConditionSpecific, feltPositiveMinusNegativeOdd, feltPositiveMinusNegativeEven) |>
  mutate(ratingSynchrony = abs(feltPositiveMinusNegativeOdd - feltPositiveMinusNegativeEven)*-1)
```


# Create synchrony and individual ratings datasets
```{r}
# Synchrony ratings
classic_neural_similarity_ratings_wide <- classic_neural_similarity_ratings |>
  select(dyad, idOdd, idEven, clips, neuralSimCondition,
         neuralSimConditionSpecific, ratingSynchrony)

perspective_neural_similarity_ratings_wide <- perspective_neural_similarity_ratings |>
  select(dyad, idOdd, idEven, clips, neuralSimCondition,
         neuralSimConditionSpecific, ratingSynchrony)

neural_similarity_ratings_wide <- full_join(classic_neural_similarity_ratings_wide,
                                            perspective_neural_similarity_ratings_wide)

neural_similarity_data_synchrony <- full_join(neural_similarity_data,
                                              neural_similarity_ratings_wide) |>
  # Fix missing ids
  mutate(idOdd = ifelse(dyad == 5, 9,
                        ifelse(dyad == 24, 47,
                               ifelse(dyad == 27, 53,
                                      ifelse(dyad == 33, 65, 
                                             idOdd)))),
         idEven = ifelse(dyad == 4, 8,
                         ifelse(dyad == 9, 18,
                                ifelse(dyad == 10, 20,
                                       ifelse(dyad == 19, 38,
                                              ifelse(dyad == 20, 40,
                                                     ifelse(dyad == 33, 66, 
                                                            idEven))))))) |>
  pivot_longer(7:8, names_to = "type", values_to = "id") |>
  select(dyad, id, ratingSynchrony, everything(), -type)

# Individual ratings
classic_neural_similarity_ratings_long <- classic_neural_similarity_ratings |>
  select(dyad, idOdd, idEven, clips, neuralSimCondition,
         neuralSimConditionSpecific, feltPositiveMinusNegativeOdd,
         feltPositiveMinusNegativeEven)

perspective_neural_similarity_ratings_long <- perspective_neural_similarity_ratings |>
  select(dyad, idOdd, idEven, clips, neuralSimCondition,
         neuralSimConditionSpecific, feltPositiveMinusNegativeOdd,
         feltPositiveMinusNegativeEven)

neural_similarity_ratings_long <- full_join(classic_neural_similarity_ratings_long,
                                            perspective_neural_similarity_ratings_long)

neural_similarity_ratings_odd <- neural_similarity_ratings_long |>
  select(dyad, idOdd, clips, neuralSimCondition, neuralSimConditionSpecific,
         feltPositiveMinusNegativeOdd) |>
  rename(id = idOdd, feltPositiveMinusNegative = feltPositiveMinusNegativeOdd)

neural_similarity_ratings_even <- neural_similarity_ratings_long |>
  select(dyad, idEven, clips, neuralSimCondition, neuralSimConditionSpecific,
         feltPositiveMinusNegativeEven) |>
  rename(id = idEven, feltPositiveMinusNegative = feltPositiveMinusNegativeEven)

neural_similarity_ratings_long <- full_join(neural_similarity_ratings_odd,
                                            neural_similarity_ratings_even)

neural_similarity_data_individual <- full_join(neural_similarity_data,
                                               neural_similarity_ratings_long) |>
  select(dyad, id, everything()) |>
  mutate(id = ifelse(dyad == 4 & is.na(id), 8, 
                     ifelse(dyad == 5 & is.na(id), 9, 
                            ifelse(dyad == 9 & is.na(id), 18,
                                   ifelse(dyad == 10 & is.na(id), 20,
                                          ifelse(dyad == 19 & is.na(id), 38,
                                                 ifelse(dyad == 20 & is.na(id), 40,
                                                        ifelse(dyad == 24 & is.na(id), 47,
                                                               ifelse(dyad == 27 & is.na(id), 53, id))))))))) |>
  mutate(id = ifelse(dyad == 33 & is.na(id) & neuralSimConditionSpecific == "odd_self_even_self",
                     66,
                     ifelse(dyad == 33 & is.na(id) & 
                              neuralSimConditionSpecific == "odd_friend_even_friend",
                     65, id)))
```


# Export
```{r}
write.csv(neural_similarity_data_synchrony, "/Users/aliciavallorani/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Research Projects/F31/BFFs/analyses/neural_similarity/data/for_analysis/neural_similarity_data_synchrony_12092023.csv", row.names = FALSE)

write.csv(neural_similarity_data_individual, "/Users/aliciavallorani/Library/CloudStorage/OneDrive-ThePennsylvaniaStateUniversity/Research Projects/F31/BFFs/analyses/neural_similarity/data/for_analysis/neural_similarity_data_individual_12092023.csv", row.names = FALSE)
```

